### 2019-12-19 paper/paper.tex
separate function translator

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[a4paper]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\usepackage[sorting=ynt,sortcites=true,backend=bibtex8,doi=false,maxnames=4,isbn=false,firstinits=true]{biblatex}
\addbibresource{reference}

\usepackage{hyperref}
\hypersetup
{
  bookmarks       = true,
  unicode         = true,
  pdftitle        = "Practical Type Blurring",
  pdfauthor       = "Ta Thanh Dinh", %auteur du document
%   pdfsubject      = "A Conceptual Approach for Message Format Extraction",
  pdftoolbar      = true, %barre d'outils non visible
  pdfmenubar      = true, %barre de menu visible
  pdfhighlight    = /O, %effet d'un clic sur un lien hypertexte
  colorlinks      = true, %couleurs sur les liens hypertextes
%   pdfpagemode = None, %aucun mode de page
%   pdfpagelayout = SinglePage, %ouverture en simple page
  pdffitwindow    = true, %pages ouvertes entierement dans toute la fenetre
  linkcolor       = red, %couleur des liens hypertextes internes
  citecolor       = green, %couleur des liens pour les citations
  urlcolor        = cyan, %couleur des liens pour les url
%   pagebackref=true
%   bookmarksdepth  = 3
}

\usepackage{listings}
\lstset{basicstyle=\small\ttfamily,showspaces=false,frame=tb}
\lstloadlanguages{C,C++,[x86masm]Assembler}

\usepackage{cleveref}

\begin{document}
%
\title{Practical Type Blurring}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Ta Thanh Dinh}
%
\authorrunning{Ta Thanh Dinh}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
\email{tathanhdinh@gmail.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
High-level type reconstruction is an important step in machine code decompilation.
Researchers show possibilities of mapping untyped machine-dependent
primitives into types of a C-like type system.

We show that the techniques used for type reconstruction can be bypassed,
and we claim that the bypass is always possible given \emph{semantics gap} between
type systems of high-level and machine language.
% \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
Binary code type inference is to restore high-level type information of variables,
functions from machine codes. It is useful for reverse code engineering (e.g.
decompilation) or static binary rewriting/instrumentation, just to name a few.
Type reconstruction is available in several binary analysis
tools~\cite{noauthor_hex-rays_nodate, noauthor_jeb_nodate, noauthor_ghidra_nodate}
as a result of machine code decompilation. Academic research includes~\cite{mycroft_type-based_1999}
which is one of the pilot papers on this domain, an improvement supporting
a limited form of subtyping is presented in~\cite{lee_tie_2011}, a survey of
research up until 2016 is given in~\cite{caballero_type_2016}. One of recent
directions is to use machine learning~\cite{maier_typeminer_2019}, which is out of scope of
the paper. All approaches tend to output a C-like type system.

Basically, the type inference starts by detecting high-level variables from
machine-dependent primitives: local variables are stored in function stack frame,
parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for example.
Type constraints are generated then through the use of these variables. Finally,
the constraints are solved, each variable is annotated with a type given by the solver.

Though most papers agree that type information is removed in compilation~\cite{lee_tie_2011,caballero_type_2016,lin_automatic_2010},
there is no explicit explication of \emph{why and how} some type information is not needed
(so removed) in machine codes. A popular point of view that types should attach with
storage specific primitives (e.g. \texttt{int} is some \texttt{32-bit} signed integer
stored in a register or stack), though mostly correct, does not reveal the nature of
types. This is one of the reasons why some researchers unify data structure reverse
engineering with type reconstruction~\cite{caballero_type_2016, caballero_polyglot_2007}.
In some languages other than C, types can be zero-sized~\cite{noauthor_phantom_nodate}, another example is
\emph{regions}~\cite{grossman_region-based_2002} which have no storage imprint.

The binary type reconstruction is influenced by \emph{Algorithm W} used originally to
type check/inference for programs of Hindley-Milner's type system (abbr. HM)~\cite{milner_theory_1978,hindley_principal_1969,cardelli_basic_1987}.
While the supposed target is a C-like type system, some authors claim to replicate
the result of \emph{principal types}~\cite{damas_principal_1982,hindley_principal_1969}
by recovering \emph{the most precise yet conservative} type~\cite{lee_tie_2011}.
Such a result is sound in a limited context only, C's type system is not HM: there
are functions that are trivially typed in C by casting, but not typeable in HM's.
Actually, it is not rare to observe type inconsistency in decompilation results
of security tools.

\paragraph{Contribution}
We first discuss the type information loss in compilation and some cases
where assigning a high-level \emph{type} for a low-level primitive
is not possible. Though this part is not novel, we bring it to the context
of binary code analysis to show limits of type reconstruction. Next, we present
a C compiler which tries to hide types from reconstruction techniques described
in current researches.

\section{Type information loss}
Type system of a language can be considered as a set or rules about constraints
on programs of this language. On statically typed languages, the constraints
can be mechanically checked and proved without running the program, it helps
avoid bugs as Robin Milner's famous slogan~\textquote{well-type program cannot go wrong}~\cite{milner_theory_1978}.

There exists at least two sources information loss: \emph{type erasure} and
\emph{data indistinguishability}~\cite{noauthor_struct_nodate}, happening at
different phases of compilation.

\subsection{Type erasure}
Once the program is type checked, the type information is normally not needed for
evaluation (i.e. running program): the compiler can select a consistent machine-dependent
representation for each high-level type, this representation may only have little
relation with the original type but it does not violate the fact that the program
is checked (then safe).

\begin{example}\label{exa:typed_enum}
\texttt{C++}'s typed enum.

\begin{lstlisting}[frame=lines, language={C++}]
enum E { one = 1, two };
void foo(enum E e) {
  switch (e) {
  case E::one:
  case E::two:
    printf("ok\n");
    break;

  default: assert(false);
  }
}

enum E bar() {...return some enum E }

int main() {
  enum E e = bar(); foo(e);
  return 0:
}
\end{lstlisting}

The program is safe when type-checked: \texttt{assert(0)} will
never be reached when the program runs. In machine code, we may observe that
\texttt{foo} is a function accepting a \texttt{32-bit} signed integer, i.e. information about
\texttt{enum E} type is erased. However there is no need to add runtime
checking for the case where \texttt{foo} is passed an argument of value not in \texttt{enum E}
(e.g. \texttt{3}), this case is eliminated by the compiler's type checker.
\end{example}

\subsection{Data indistinguishability}
When generating binary code for a specific hardware/operating system, the compiler will
use a consistent representation for low-level primitives (e.g. registers used in
function parameters or return value, alignment for fields of aggregate types), so that
the output binary can be used by other programs on the same system. It it possible that
two types are distinguished at high-level but they have the same data representation
at low-level.

\begin{example}\label{exa:register_struct}
Small struct passing.

\begin{lstlisting}[frame=lines, language={C}]
struct S { int a; int b; };
int foo(struct S s) {
  return s.a + s.b;
}

int bar(long long l) {
  return (int)l + (int)(l >> 32);
}
\end{lstlisting}

Under System V AMD64 ABI~\cite{lu_system_nodate}, the aggregate type \texttt{S}
has class \texttt{INTEGER}: the argument \texttt{s} is passed just in register \texttt{rdi}.
At the ABI level, \texttt{foo} and \texttt{bar} is interchangeable, but they are not at
the type level.
\end{example}

\subsection{Untypeable}

There is no type casting in Hindley-Milner's type system (abbr. HM), so when using a variant of
\emph{Algorithm-W}~\cite{milner_theory_1978} for binary code type inference, the output (as a
C program without type casting) may not exist: there are programs which are
trivially typed in C, but not in HM.

\begin{example}\label{exa:untypeable}
Untypeable function.
\begin{lstlisting}[frame=topline, language={C}]
int foo(int i, int *f) {
  return ((int (*)(int (*)(int, int*), int))f)(foo, i);
}
\end{lstlisting}
Disassembled code:
\begin{lstlisting}[frame=bottomline, language={[x86masm]Assembler}]
0x0     55                               push rbp
0x1     48 89 e5                         mov rbp, rsp
0x4     48 83 ec 10                      sub rsp, 0x10
0x8     89 7d fc                         mov [rbp-0x4], edi
0xb     48 89 75 f0                      mov [rbp-0x10], rsi
0xf     48 8b 45 f0                      mov rax, [rbp-0x10]
0x13    8b 75 fc                         mov esi, [rbp-0x4]
0x16    48 bf 00 00 00 00 00 00 00 00    mov rdi, 0x0
0x20    ff d0                            call rax
0x22    48 83 c4 10                      add rsp, 0x10
0x26    5d                               pop rbp
0x27    c3                               ret
\end{lstlisting}

From disassembled code, it is direct to detect that the second argument
of \texttt{foo} is of functional type (since \texttt{call rax} at address \texttt{0x20}),
but assigning an functional type for \texttt{f} is not possible.
\end{example}

The inevitability of type information loss means that the binary code
type reconstruction cannot always reaches the notion of
\emph{the most precise yet conservative type}~\cite{lee_tie_2011}. Since
compilation is a \textquote{many-to-one mapping}~\cite{mycroft_type-based_1999},
real world decompilers simply look for one of possible maps,
sometimes they accept even inconsistencies in reconstructed types.

\section{Untyped C}

% \emph{well-type program cannot go wrong}, or even leads to better optimization.

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\printbibliography
\end{document}

### 2019-12-19 src/backend/support.rs

@@ -7,11 +7,20 @@ use cranelift_simplejit::SimpleJITBackend;
 
 use crate::{
 	checked_if_let, checked_unwrap,
-	frontend::syntax::{Declaration, Declarator, Identifier, StructType, TypeSpecifier},
+	frontend::syntax::{
+		BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression,
+		Identifier, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+	},
 };
 
-// Engineering a Compiler: 7.7.1 Understanding Structure Layout
-// Dragon Book: 6.3.4 Storage Layouts for Local Names
+pub enum SimpleConcreteType {
+	ConstantTy(i64),
+	ValueTy(Value),
+	StackSlotTy(StackSlot),
+	UnitTy,
+}
+// EaC 7.7.1 Understanding Structure Layout
+// DRAGON 6.3.4 Storage Layouts for Local Names
 #[derive(Clone)]
 pub struct AggregateType<'a> {
 	pub fields: Vec<(&'a str, Type)>,
@@ -36,7 +45,9 @@ impl AggregateType<'_> {
 	}
 
 	pub fn bytes(&self) -> usize {
-		self.fields.iter().fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize)
+		self.fields
+			.iter()
+			.fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize)
 	}
 }
 
@@ -47,11 +58,21 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 		let declarations = checked_unwrap!(declarations.as_ref());
 		let fields: Vec<(&str, Type)> = declarations
 			.iter()
-			.map(|Declaration { specifier, declarator }| {
-				checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, {
-					(*ident, specifier.into())
-				})
-			})
+			.map(
+				|Declaration {
+				     specifier,
+				     declarator,
+				 }| {
+					checked_if_let!(
+						Some(Declarator {
+							ident: Identifier(ident),
+							..
+						}),
+						declarator,
+						{ (*ident, specifier.into()) }
+					)
+				},
+			)
 			.collect();
 		AggregateType { fields }
 	}
@@ -59,7 +80,7 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 
[…]

### 2019-12-19 src/backend/translation.rs

@@ -21,11 +21,16 @@ use crate::{
 	unimpl,
 };
 
-use super::support::{
-	AggregateIdentifier, AggregateType, ConcreteModule, FunctionIdentifier, FunctionType,
-	NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleType,
-	SimpleTypedIdentifier, TypeBindingEnvironment,
+use super::{
+	function::translate_function,
+	support::{
+		evaluate_constant_arithmetic_expression, AggregateIdentifier, AggregateType,
+		ConcreteModule, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer,
+		PrimitiveIdentifier, SimpleType, SimpleTypedIdentifier, TypeBindingEnvironment,
+	},
 };
+
+// use super::function::*;
 
 static NEW_VAR_ID: AtomicUsize = AtomicUsize::new(0);
 
@@ -38,42 +43,6 @@ fn type_cast_value<'clif>(val: Value, ty: Type, func_builder: &'clif mut Functio
 		func_builder.ins().sextend(ty, val)
 	} else {
 		val
-	}
-}
-
-fn evaluate_constant_arithmetic_expression(expr: &'_ Expression) -> Option<i64> {
-	use Expression::*;
-
-	match expr {
-		ConstantExpr(Constant::IntegerConst(i)) => Some(i.into()),
-
-		UnaryOperatorExpr(UnaryOperatorExpression { operator, operand }) => {
-			use UnaryOperator::*;
-
-			let val = evaluate_constant_arithmetic_expression(operand.as_ref())?;
-			match operator {
-				Negation => Some(-val),
-				PreIncrement => Some(val + 1),
-				PostIncrement => Some(val),
-				Address => None,
-			}
-		}
-
-		BinaryOperatorExpr(BinaryOperatorExpression { operator, lhs, rhs }) => {
-			use BinaryOperator::*;
-
-			let lval = evaluate_constant_arithmetic_expression(lhs.as_ref())?;
-			let rval = evaluate_constant_arithmetic_expression(rhs.as_ref())?;
-			match operator {
-				Multiplication => Some(lval * rval),
-				Division => Some(lval / rval),
-				Addition => Some(lval + rval),
-				Subtraction => Some(lval - rval),
-				_ => None,
-			}
-		}
-
-		_ => None,
 	}
 }
 
[…]

### 2020-01-08 paper/paper.tex
blur some types

@@
   unicode         = true,
-  pdftitle        = "Practical Type Blurring",
+  pdftitle        = "Practical Type Flattening",
   pdfauthor       = "Ta Thanh Dinh", %auteur du document
@@
 %
-\title{Practical Type Blurring}
+\title{Practical Type Flattening}
 %
@@
 \section{Introduction}
-Binary code type inference is to restore high-level type information of variables,
+Binary code type recovery is to restore high-level type information of variables,
 functions from machine codes. It is useful for reverse code engineering (e.g.
 decompilation) or static binary rewriting/instrumentation, just to name a few.
-Type reconstruction is available in several binary analysis
+Type recovery is available in several binary analysis
 tools~\cite{noauthor_hex-rays_nodate, noauthor_jeb_nodate, noauthor_ghidra_nodate}
-as a result of machine code decompilation. Academic research includes~\cite{mycroft_type-based_1999}
-which is one of the pilot papers on this domain, an improvement supporting
-a limited form of subtyping is presented in~\cite{lee_tie_2011}, a survey of
-research up until 2016 is given in~\cite{caballero_type_2016}. One of recent
-directions is to use machine learning~\cite{maier_typeminer_2019}, which is out of scope of
-the paper. All approaches tend to output a C-like type system.
+as a result of machine code decompilation. Academic research includes the classic
+paper of Mycroft~\cite{mycroft_type-based_1999} which is probably the first work
+on the domain, though earlier ideas~\cite{shivers_data-flow_1990} have been used
+to recover types of programs in Scheme - a dynamically typed language.
+Lee et al.~\cite{lee_tie_2011} introduces
+an extension for Mycroft's work which supports a limited form of subtyping.
+Caballero and Lin give a survey~\cite{caballero_type_2016} for research up until 2015.
+Recent directions are using machine learning~\cite{maier_typeminer_2019} or statistical
+language model~\cite{katz_estimating_2016}, which are out of scope of the paper.
+All approaches tend to output a C-like type system.
 
-Basically, the type inference starts by detecting high-level variables from
+Basically, the binary code type recovery starts by detecting high-level objects from
 machine-dependent primitives: local variables are stored in function stack frame,
-parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for example.
-Type constraints are generated then through the use of these variables. Finally,
-the constraints are solved, each variable is annotated with a type given by the solver.
+parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for related techniques.
+Type constraints are generated gradually through the \empĥ{low-level use} of objects.
+The system of constraints is solved then, each object is assigned a certain
+(polymorphic) type.
 
-Though most papers agree that type information is removed in compilation~\cite{lee_tie_2011,caballero_type_2016,lin_automatic_2010},
-there is no explicit explication of \emph{why and how} some type information is not needed
-(so removed) in machine codes. A popular point of view that types should attach with
-storage specific primitives (e.g. \texttt{int} is some \texttt{32-bit} signed integer
-stored in a register or stack), though mostly correct, does not reveal the nature of
-types. This is one of the reasons why some researchers unify data structure reverse
-engineering with type reconstruction~\cite{caballero_type_2016, caballero_polyglot_2007}.
-In some languages other than C, types can be zero-sized~\cite{noauthor_phantom_nodate}, another example is
-\emph{regions}~\cite{grossman_region-based_2002} which have no storage imprint.
+This bird view may give off an impression that the
+binary code type reconstruction is a well established research domain, incorrect results
+are because of foreign reasons: incorrect binary code disassembling,
+high-level variable detection, etc. But we claim that there are probably intrinsic problems.
 
-The binary type reconstruction is influenced by \emph{Algorithm W} used originally to
-type check/inference for programs of Hindley-Milner's type system (abbr. HM)~\cite{milner_theory_1978,hindley_principal_1969,cardelli_basic_1987}.
-While the supposed target is a C-like type system, some authors claim to replicate
-the result of \emph{principal types}~\cite{damas_principal_1982,hindley_principal_1969}
-by recovering \emph{the most precise yet conservative} type~\cite{lee_tie_2011}.
-Such a result is sound in a limited context only, C's type system is not HM: there
-are functions that are trivially typed in C by casting, but not typeable in HM's.
-Actually, it is not rare to observe type inconsistency in decompilation results
+\emph{First}, there is a common agreement that type information is removed through
+compilation~\cite{lee_tie_2011,caballero_type_2016,lin_automatic_2010},
+but there is no explicit explication of why and how some type information is not needed,
+so removed, in machine codes. The result of reconstructing \emph{the most precise yet conservative}
+type~\cite{lee_tie_2011}, which may suggest the well-known
+\emph{principal types}~\cite{damas_principal_1982,hindley_principal_1969},
+is sound in a limited context only. Actually not all type
+information can be restored.
+
+\emph{Second}, though some techniques of data structure reverse
+engineering~\cite{caballero_type_2016, caballero_polyglot_2007} can be reused for
+type recovery, types do not always attach with storage specific primitives (for example
+\texttt{int} is some \texttt{32-bit} signed integer stored in a register or stack).
+The storage-based point of view is almost correct in low-level languages like C, it
+does not reveal the nature of types. In other languages, types can be
+zero-sized~\cite{noauthor_phantom_nodate}, another examples are
+\emph{regions}~\cite{grossman_region-based_2002} or \emph{units-of-measure}~\cite{kennedy_types_2010}
+which leave no storage imprint.
+
+\emph{Third}, current research uses some variants of
+\emph{Algorithm W}~\cite{milner_theory_1978,cardelli_basic_1987} to resolve type
+constraints in a C-like language. But the polymorphism in C is rather
+\emph{ad-hoc}~\cite{strachey_fundamental_2000}: some functions are
+trivially typed in C by casting, but not typeable in Hindley-Milner type system. This
+problem is remarked already in~\cite{mycroft_type-based_1999}, but unfortunately omitted in
+later extension~\cite{lee_tie_2011}. In real world, it is not rare to see type inconsistency in decompilation results
 of security tools.
+
+% used originally to
+% type check/inference for programs of Hindley-Milner's type system (abbr. HM).
+% While the supposed target is a C-like type system, some authors claim to replicate
+% the result of \emph{principal types}~\cite{damas_principal_1982,hindley_principal_1969}
+% by recovering \emph{the most precise yet conservative} type~\cite{lee_tie_2011}.
+% Such a result is sound in a limited context only, C's type system is not HM: there
+% are functions that are trivially typed in C by casting, but not typeable in HM's.
+% Actually, it is not rare to observe type inconsistency in decompilation results
+% of security tools.
 
@@
 of binary code analysis to show limits of type reconstruction. Next, we present
-a C compiler which tries to hide types from reconstruction techniques described
+a proof-of-concept C compiler which tries to hide types from reconstruction techniques described
 in current researches.
@@
 \section{Type information loss}
-Type system of a language can be considered as a set or rules about constraints
-on programs of this language. On statically typed languages, the constraints
-can be mechanically checked and proved without running the program, it helps
-avoid bugs as Robin Milner's famous slogan~\textquote{well-type program cannot go wrong}~\cite{milner_theory_1978}.
+Informally speaking, a type system is some set of constraints and rules to infer constraints
+on a program. The type system decides which are allowed or forbidden on the semantics of the language,
+for example adding two pointers is not allowed in C because this operation is semantically nonsense.
+Type helps avoid bugs as summarized in Milner's famous
+slogan~\textquote{well-type program cannot go wrong}~\cite{milner_theory_1978}.
 
-There exists at least two sources information loss: \emph{type erasure} and
-\emph{data indistinguishability}~\cite{noauthor_struct_nodate}, happening at
-different phases of compilation.
+In statically typed languages, the compiler checks the type constraints then generates
+machine codes (we consider here only languages which generates machine codes), but then
+most of constraints are lost because they are not needed for running
+the program. There are at least two sources of
+information loss: \emph{type erasure} and \emph{data indistinguishability},
+happening at different phases of compilation.
 
 \subsection{Type erasure}
-Once the program is type checked, the type information is normally not needed for
-evaluation (i.e. running program): the compiler can select a consistent machine-dependent
+\emph{Type erasure} means the "intensional" type of an object is hidden/inaccessible or
+completely removed in some context. It appears under several concepts: subtype substitution,
+generic specialization (or monomorphization), or boxing, just name a few. In some cases,
+e.g. subtype substitution, the (sub)type of the wrapped object does not completely removed,
+it is just not accessible in contexts where only behaviors of the super type are allowed.
+Such a case will not be discussed in the paper since we look at the low-level machine code.
+
+Once the program is type checked,
+% the type information is normally not needed for evaluation (i.e. running program),
+ the compiler will select a consistent machine-dependent
 representation for each high-level type, this representation may only have little
 relation with the original type but it does not violate the fact that the program
-is checked (then safe).
+is checked, then safe.
 

### 2020-01-08 src/backend.rs

@@ -2,9 +2,7 @@
 //  - ir translation
 //  - machine code generation
 
-use cranelift_codegen::ir::Function;
-use cranelift_module::FuncId;
-use cranelift_simplejit::SimpleJITBuilder;
+use cranelift_module::{Backend, FuncId, Module};
 
 mod function;
 mod support;
@@ -12,21 +10,20 @@ mod translation;
 
 use crate::frontend::syntax::TranslationUnit;
 use support::{
-	ConcreteModule, FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier,
-	TypeBindingEnvironment,
+	FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment,
 };
 
 // an abstract machine that runs Cranelift IR
-pub struct AbstractMachine<'s> {
-	module: ConcreteModule,
+pub struct AbstractMachine<'s, B: Backend> {
+	module: Module<B>,
 	name_env: NameBindingEnvironment<'s>,
 	compiled_funcs: Vec<(FuncId, usize)>,
 }
 
-impl<'s> AbstractMachine<'s> {
-	pub fn new(tu: &'s TranslationUnit) -> Self {
-		let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
-		let mut module = ConcreteModule::new(builder);
+impl<'s, B: Backend> AbstractMachine<'s, B> {
+	pub fn new(tu: &'s TranslationUnit, builder: B::Builder) -> Self {
+		// let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
+		let mut module = Module::new(builder);
 		let mut name_env = NameBindingEnvironment::new();
 		let mut type_env = TypeBindingEnvironment::new();
 		let compiled_funcs = translation::compile(tu, &mut module, &mut name_env, &mut type_env);
@@ -34,14 +31,19 @@ impl<'s> AbstractMachine<'s> {
 		AbstractMachine { module, name_env, compiled_funcs }
 	}
 
-	pub fn compiled_function(&mut self, fname: &'_ str) -> Option<&[u8]> {
-		let ident = self.name_env.get(fname)?;
+	pub fn compiled_function(&mut self, fname: &'_ str) -> Option<(B::FinalizedFunction, usize)> {
+		let ident = self.name_env.get(fname);
[…]

### 2020-01-08 src/backend/function.rs

@@ -1,123 +1,267 @@
-#![allow(dead_code)]
-
 use std::{
 	cell::RefCell,
-	cmp,
+	collections::HashMap,
 	hint::unreachable_unchecked,
 	i16, i32, i64, i8,
-	marker::PhantomData,
-	mem, slice,
 	sync::atomic::{AtomicUsize, Ordering},
 };
 
 use cranelift::prelude::*;
 use cranelift_codegen::{
-	ir::{entities::StackSlot, Function, Inst},
+	ir::{
+		entities::{FuncRef, SigRef, StackSlot},
+		Inst,
+	},
 	Context,
 };
-use cranelift_module::{FuncId, Linkage};
+use cranelift_module::{Backend, FuncId, Linkage, Module};
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap, error,
+	checked_if_let, checked_match, checked_unwrap_option, checked_unwrap_result,
 	frontend::syntax::{
-		BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator,
-		DoWhileStatement, Expression, ExternalDeclaration, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier,
-		IfStatement, Integer, MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier,
+		BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration,
+		Declarator, DerivedDeclarator, DoWhileStatement, Expression, ExternalDeclaration,
+		ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, Integer,
+		MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier,
 		UnaryOperator, UnaryOperatorExpression, WhileStatement,
 	},
-	unimpl,
+	generate_random_maps, unimpl,
 };
 
 use super::support::{
-	evaluate_constant_arithmetic_expression, AggregateIdentifier, AggregateType, ConcreteModule, FunctionIdentifier,
-	FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleConcreteType, SimpleType,
-	SimpleTypedIdentifier, TypeBindingEnvironment,
[…]

### 2020-01-08 src/backend/support.rs

@@ -2,14 +2,19 @@ use std::{collections::HashMap, hint::unreachable_unchecked};
 
 use cranelift::prelude::*;
 use cranelift_codegen::ir::entities::StackSlot;
-use cranelift_module::{FuncId, Module};
-use cranelift_simplejit::SimpleJITBackend;
+use cranelift_module::FuncId;
+
+use rand::{thread_rng, Rng};
 
 use crate::{
-	checked_if_let, checked_unwrap,
-	frontend::syntax::{
-		BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression,
-		Identifier, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+	checked_if_let, checked_unwrap_option,
+	frontend::{
+		semantics::Environment,
+		syntax::{
+			BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator,
+			Expression, Identifier, StructType, TypeSpecifier, UnaryOperator,
+			UnaryOperatorExpression,
+		},
 	},
 };
 
@@ -21,7 +26,7 @@ pub enum SimpleConcreteType {
 }
 // EaC 7.7.1 Understanding Structure Layout
 // DRAGON 6.3.4 Storage Layouts for Local Names
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub struct AggregateType<'a> {
 	pub fields: Vec<(&'a str, Type)>,
 }
@@ -45,9 +50,7 @@ impl AggregateType<'_> {
 	}
 
 	pub fn bytes(&self) -> usize {
-		self.fields
-			.iter()
-			.fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize)
+		self.fields.iter().fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize)
 	}
 }
 
@@ -55,36 +58,26 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 	fn into(self) -> AggregateType<'a> {
 		// struct type definition: each declaration is a field declaration
 		let StructType { declarations, .. } = self;
-		let declarations = checked_unwrap!(declarations.as_ref());
+		let declarations = checked_unwrap_option!(declarations.as_ref());
[…]

### 2020-01-08 src/backend/translation.rs

@@ -1,1168 +1,69 @@
-use std::{
-	cmp,
-	hint::unreachable_unchecked,
-	i16, i32, i64, i8, mem, slice,
-	sync::atomic::{AtomicUsize, Ordering},
-};
+use std::hint::unreachable_unchecked;
 
-use cranelift::prelude::*;
-use cranelift_codegen::{ir::Function, Context};
-use cranelift_module::{FuncId, Linkage};
+use cranelift_module::{Backend, FuncId, Linkage, Module};
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap, error,
+	checked_match, checked_unwrap_result,
 	frontend::syntax::{
-		BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration,
-		Declarator, DerivedDeclarator, DoWhileStatement, Expression, ExternalDeclaration,
-		ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, Integer,
-		MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier,
-		UnaryOperator, UnaryOperatorExpression, WhileStatement,
+		Declaration, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier,
+		StructType, TranslationUnit, TypeSpecifier,
 	},
-	unimpl,
 };
 
 use super::{
-	function::translate_function,
+	function::{blur_function_signature, get_function_signature, translate_function},
 	support::{
-		evaluate_constant_arithmetic_expression, AggregateIdentifier, AggregateType,
-		ConcreteModule, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer,
-		PrimitiveIdentifier, SimpleType, SimpleTypedIdentifier, TypeBindingEnvironment,
+		AggregateType, FunctionIdentifier, FunctionType, NameBindingEnvironment, SimpleType,
+		SimpleTypedIdentifier, TypeBindingEnvironment,
 	},
 };
 
-// use super::function::*;
-
-static NEW_VAR_ID: AtomicUsize = AtomicUsize::new(0);
-
-fn type_cast_value<'clif>(val: Value, ty: Type, func_builder: &'clif mut FunctionBuilder) -> Value {
-	let val_size = func_builder.func.dfg.value_type(val).bytes();
-	let ty_size = ty.bytes();
-	if val_size > ty_size {
[…]

### 2020-01-08 src/frontend/semantics.rs

@@ -18,20 +18,21 @@ use super::syntax::{
 	TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
 };
 
-use crate::{checked_if_let, checked_match, checked_unwrap, error, unimpl};
+use crate::{checked_if_let, checked_match, checked_unwrap_option, error, unimpl};
 
+#[derive(Clone, Debug)]
 pub struct Environment<'a, K, Ty>
 where
-	K: 'a + Copy + Eq + Hash,
+	K: 'a + Copy + Eq + Hash + std::fmt::Debug,
 	Ty: 'a + Clone,
 {
 	pub env: HashMap<K, BoundedType<Ty>>,
 	phantom: PhantomData<&'a K>,
 }
 
-#[derive(Clone, Copy, PartialEq, Eq, Hash)]
+#[derive(Clone, Copy, Debug, PartialEq, Eq, Hash)]
 pub struct IdentifierName<'a>(&'a str);
-#[derive(Clone, Copy, PartialEq, Eq, Hash)]
+#[derive(Clone, Copy, Debug, PartialEq, Eq, Hash)]
 pub struct TypeName<'a>(&'a str);
 
 impl Borrow<str> for &'_ IdentifierName<'_> {
@@ -114,14 +115,11 @@ impl<'a> AsRef<str> for Identifier<'a> {
 
 impl<'a, K, T> Environment<'a, K, T>
 where
-	K: 'a + Clone + Copy + Eq + Hash + AsRef<str>,
+	K: 'a + Clone + Copy + std::fmt::Debug + Eq + Hash + AsRef<str>,
 	T: 'a + Clone,
 {
 	pub fn new() -> Self {
-		Self {
-			env: HashMap::new(),
-			phantom: PhantomData,
-		}
+		Self { env: HashMap::new(), phantom: PhantomData }
 	}
 
 	pub fn inherit(&self) -> Self {
@@ -129,10 +127,7 @@ where
 		for (name, _) in &self.env {
 			inherited_env.get_mut(name).unwrap().rebind = false
 		}
-		Self {
-			env: inherited_env,
-			phantom: PhantomData,
-		}
+		Self { env: inherited_env, phantom: PhantomData }
 	}
 
 	pub fn bind(&mut self, name: K, ty: T) {
@@ -149,6 +144,13 @@ where
 			.map(|BoundedType { ty, .. }| ty)
[…]

### 2020-01-08 src/frontend/syntax.rs

@@ -4,7 +4,7 @@ use std::hint::unreachable_unchecked;
 use crate::error;
 
 const KEYWORDS: &'_ [&'_ str] = &[
-	"if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void"
+	"if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void",
 ];
 
 #[derive(Clone)]
@@ -25,6 +25,7 @@ pub struct UnaryOperatorExpression<'a> {
 pub enum BinaryOperator {
 	Multiplication,
 	Division,
+	Remainder,
 	Addition,
 	Subtraction,
 	Less,
@@ -370,6 +371,13 @@ peg::parser! {grammar parser() for str {
 				rhs: Box::new(b),
 			})
 		}
+		a:(@) blank()* "%" blank()* b:@ {
+			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
+				operator: BinaryOperator::Remainder,
+				lhs: Box::new(a),
+				rhs: Box::new(b),
+			})
+		}
 		--
 		i:identifier() "(" blank()* es:expression() ** "," blank()* ")" {
 			Expression::CallExpr(CallExpression {
@@ -419,7 +427,7 @@ peg::parser! {grammar parser() for str {
 			})
 		}
 		--
-		i:identifier() {
+		i:identifier() blank()* {
 			Expression::IdentifierExpr(i)
 		}
 		--

### 2020-01-08 src/helper.rs

@@ -13,9 +13,16 @@ macro_rules! unimpl {
 }
 
 #[macro_export]
-macro_rules! checked_unwrap {
+macro_rules! checked_unwrap_option {
 	($expr:expr) => {
 		$expr.unwrap_or_else(|| unsafe { unreachable_unchecked() })
+	};
+}
+
+#[macro_export]
+macro_rules! checked_unwrap_result {
+	($expr:expr) => {
+		$expr.unwrap_or_else(|_| unsafe { unreachable_unchecked() })
 	};
 }
 
@@ -26,7 +33,7 @@ macro_rules! checked_if_let {
 			$block
 		} else {
 			unsafe { unreachable_unchecked() }
-		}
+			}
 	};
 }
 
@@ -36,6 +43,6 @@ macro_rules! checked_match {
 		match $expr {
 			$pat => $block,
 			_ => unsafe { unreachable_unchecked() },
-		}
+			}
 	};
 }

### 2020-01-08 src/main.rs

@@ -1,4 +1,16 @@
-use std::{fs, path::PathBuf};
+use std::{
+	fs::{self, File},
+	hint::unreachable_unchecked,
+	mem,
+	path::PathBuf,
+	slice,
+	str::FromStr,
+};
+
+use cranelift::prelude::*;
+use cranelift_faerie::{FaerieBackend, FaerieBuilder, FaerieTrapCollection};
+use cranelift_simplejit::{SimpleJITBackend, SimpleJITBuilder};
+use target_lexicon::triple;
 
 use zydis::{
 	AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer,
@@ -20,55 +32,96 @@ struct Opt {
 
 	/// Function
 	#[structopt(name = "function", short = "f")]
-	fname: String,
+	fname: Option<String>,
+
+	/// JIT compilation
+	#[structopt(name = "code generation mode", short = "j")]
+	jit: bool,
 }
 
 fn main() {
 	let opt = Opt::from_args();
-	let (src, fname) = { (opt.src.as_path(), opt.fname.as_str()) };
+	let src = opt.src.as_path();
 
-	let src_code = fs::read_to_string(src).expect("Failed to read source code file");
+	let src_code = fs::read_to_string(src).expect("failed to read source code file");
 	let tu = frontend::syntax::parse(src_code.as_str());
 	frontend::semantics::check(&tu);
 
-	let mut am = backend::AbstractMachine::new(&tu);
-	if let Some(fptr) = am.compiled_function(fname) {
-		// println!("{}", &fclif);
+	if opt.jit {
+		let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
+		let mut am = backend::AbstractMachine::<'_, SimpleJITBackend>::new(&tu, builder);
+		if let Some(fname) = &opt.fname {
+			if let Some((fptr, flen)) = am.compiled_function(fname.as_str()) {
+				let fptr = unsafe {
+					slice::from_raw_parts(mem::transmute::<_, *const u8>(fptr), flen as _)
+				};
 
-		let asm_formatter = {
-			let mut fm =
-				Formatter::new(FormatterStyle::INTEL).expect("failed to create assembly formatter");
-			fm.set_property(FormatterProperty::HexUppercase(false))
-				.expect("failed to disable hex uppercase");
-			fm.set_property(FormatterProperty::DisplacementSignedness(
-				Signedness::SIGNED,
-			))
[…]

### 2020-01-08 tests/14.c

@@ -1,0 +1,3 @@
+int foo(int i, int j) {
+	return (i * 5) % j;
+}

### 2020-01-08 tests/15.c

@@ -1,0 +1,12 @@
+int foo(int foo, int j) {
+	return foo + j;
+}
+
+int bar(int j) {
+	return foo(j, 88);
+}
+
+int foobar(int j) {
+	int i = bar(foo(j ,77));
+	return i + bar(i);
+}

### 2020-01-08 tests/16.c

@@ -1,0 +1,3 @@
+int foo(int *i) {
+	return i + 1;
+}

### 2020-01-08 paper/paper.tex
signature blurring

--- 2019-12-19 paper/paper.tex
@@
 as a result of machine code decompilation. Academic research includes~\cite{mycroft_type-based_1999}
-which is one of the pilot papers on this domain, an improvement supporting
+which was probably the pilot paper on the domain, an extension supporting
 a limited form of subtyping is presented in~\cite{lee_tie_2011}, a survey of
-research up until 2016 is given in~\cite{caballero_type_2016}. One of recent
-directions is to use machine learning~\cite{maier_typeminer_2019}, which is out of scope of
-the paper. All approaches tend to output a C-like type system.
+research up until 2015 is given in~\cite{caballero_type_2016}. Recent
+directions are using machine learning~\cite{maier_typeminer_2019} or statistical
+language model~\cite{katz_estimating_2016}. All approaches tend to output a C-like type system.
 
@@
 
-Though most papers agree that type information is removed in compilation~\cite{lee_tie_2011,caballero_type_2016,lin_automatic_2010},
-there is no explicit explication of \emph{why and how} some type information is not needed
-(so removed) in machine codes. A popular point of view that types should attach with
-storage specific primitives (e.g. \texttt{int} is some \texttt{32-bit} signed integer
-stored in a register or stack), though mostly correct, does not reveal the nature of
-types. This is one of the reasons why some researchers unify data structure reverse
-engineering with type reconstruction~\cite{caballero_type_2016, caballero_polyglot_2007}.
-In some languages other than C, types can be zero-sized~\cite{noauthor_phantom_nodate}, another example is
-\emph{regions}~\cite{grossman_region-based_2002} which have no storage imprint.
+This bird view about binary code type reconstruction may give an impression that the
+research domain has been well established already, the incorrectness comes from foreign
+reasons: binary code disassembly, high-level variable detection, etc.
+But there are more intrinsic problems, as we claim below.
+
+\emph{First}, there is a common agreement that type information is removed through compilation~\cite{lee_tie_2011,caballero_type_2016,lin_automatic_2010},
+but there is no explicit explication of why and how some type information is not needed
+(so removed) in machine codes, actually not all type information can be restored.
+
+\emph{Second}, while some researchers unify data structure reverse engineering with
+type reconstruction~\cite{caballero_type_2016, caballero_polyglot_2007}, types do not
+always attach with storage specific primitives (e.g. \texttt{int} is some \texttt{32-bit}
+signed integer stored in a register or stack). The storage-based point of view though
+mostly correct in low-level languages like C, does not reveal the nature of types. In
+some languages other than C, types can be zero-sized~\cite{noauthor_phantom_nodate},
+another example is \emph{regions}~\cite{grossman_region-based_2002} which have no
+storage imprint.
 

### 2020-01-08 src/backend.rs

@@ -3,7 +3,7 @@
 //  - machine code generation
 
 use cranelift_codegen::ir::Function;
-use cranelift_module::FuncId;
+use cranelift_module::{FuncId, Module, Backend};
 use cranelift_simplejit::SimpleJITBuilder;
 
 mod function;
@@ -12,21 +12,21 @@ mod translation;
 
 use crate::frontend::syntax::TranslationUnit;
 use support::{
-	ConcreteModule, FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier,
+	JitModule, FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier,
 	TypeBindingEnvironment,
 };
 
 // an abstract machine that runs Cranelift IR
-pub struct AbstractMachine<'s> {
-	module: ConcreteModule,
+pub struct AbstractMachine<'s, B: Backend> {
+	module: Module<B>,
 	name_env: NameBindingEnvironment<'s>,
 	compiled_funcs: Vec<(FuncId, usize)>,
 }
 
-impl<'s> AbstractMachine<'s> {
-	pub fn new(tu: &'s TranslationUnit) -> Self {
-		let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
-		let mut module = ConcreteModule::new(builder);
+impl<'s, B: Backend> AbstractMachine<'s, B> {
+	pub fn new(tu: &'s TranslationUnit, builder: B::Builder) -> Self {
+		// let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
+		let mut module = Module::new(builder);
 		let mut name_env = NameBindingEnvironment::new();
 		let mut type_env = TypeBindingEnvironment::new();
 		let compiled_funcs = translation::compile(tu, &mut module, &mut name_env, &mut type_env);
@@ -34,14 +34,19 @@ impl<'s> AbstractMachine<'s> {
 		AbstractMachine { module, name_env, compiled_funcs }
 	}
 
-	pub fn compiled_function(&mut self, fname: &'_ str) -> Option<&[u8]> {
+	pub fn compiled_function(&mut self, fname: &'_ str) -> Option<(B::FinalizedFunction, usize)> {
 		let ident = self.name_env.get(fname)?;
 		if let SimpleTypedIdentifier::FunctionIdent(FunctionIdentifier { ident, .. }) = ident {
[…]

### 2020-01-08 src/backend/function.rs

@@ -3,6 +3,7 @@
 use std::{
 	cell::RefCell,
 	cmp,
+	collections::HashMap,
 	hint::unreachable_unchecked,
 	i16, i32, i64, i8,
 	marker::PhantomData,
@@ -12,13 +13,18 @@ use std::{
 
 use cranelift::prelude::*;
 use cranelift_codegen::{
-	ir::{entities::StackSlot, Function, Inst},
+	ir::{
+		entities::{FuncRef, SigRef, StackSlot},
+		Function, Inst,
+	},
 	Context,
 };
-use cranelift_module::{FuncId, Linkage};
+use cranelift_module::{FuncId, Linkage, Module, Backend};
+
+use rand::prelude::*;
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap, error,
+	checked_if_let, checked_match, checked_unwrap_option, checked_unwrap_result,
 	frontend::syntax::{
 		BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator,
 		DoWhileStatement, Expression, ExternalDeclaration, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier,
@@ -29,16 +35,19 @@ use crate::{
 };
 
 use super::support::{
-	evaluate_constant_arithmetic_expression, AggregateIdentifier, AggregateType, ConcreteModule, FunctionIdentifier,
+	evaluate_constant_arithmetic_expression, AggregateIdentifier, AggregateType, JitModule, FunctionIdentifier,
 	FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleConcreteType, SimpleType,
 	SimpleTypedIdentifier, TypeBindingEnvironment,
 };
 
 static NEW_VAR_ID: AtomicUsize = AtomicUsize::new(0);
 
-struct FunctionTranslator<'clif, 'tcx> {
+struct FunctionTranslator<'clif, 'tcx, B: Backend> {
 	pub func_builder: RefCell<FunctionBuilder<'clif>>,
-	module: &'clif mut ConcreteModule,
+	module: &'clif mut Module<B>,
+	func_id: FuncId,
+	func_ref: FuncRef,
+	imported_sigs: RefCell<HashMap<Signature, SigRef>>,
 	name_env: NameBindingEnvironment<'tcx>,
[…]

### 2020-01-08 src/backend/support.rs

@@ -6,7 +6,7 @@ use cranelift_module::{FuncId, Module};
 use cranelift_simplejit::SimpleJITBackend;
 
 use crate::{
-	checked_if_let, checked_unwrap,
+	checked_if_let, checked_unwrap_option,
 	frontend::syntax::{
 		BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression,
 		Identifier, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
@@ -55,7 +55,7 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 	fn into(self) -> AggregateType<'a> {
 		// struct type definition: each declaration is a field declaration
 		let StructType { declarations, .. } = self;
-		let declarations = checked_unwrap!(declarations.as_ref());
+		let declarations = checked_unwrap_option!(declarations.as_ref());
 		let fields: Vec<(&str, Type)> = declarations
 			.iter()
 			.map(
@@ -144,7 +144,7 @@ pub type NameBindingEnvironment<'a> = HashMap<&'a str, SimpleTypedIdentifier<'a>
 pub type TypeBindingEnvironment<'a> = HashMap<&'a str, SimpleType<'a>>;
 
 // backend-ed module
-pub type ConcreteModule = Module<SimpleJITBackend>;
+pub type JitModule = Module<SimpleJITBackend>;
 
 pub fn evaluate_constant_arithmetic_expression(expr: &'_ Expression) -> Option<i64> {
 	use Expression::*;

### 2020-01-08 src/backend/translation.rs

@@ -7,10 +7,10 @@ use std::{
 
 use cranelift::prelude::*;
 use cranelift_codegen::{ir::Function, Context};
-use cranelift_module::{FuncId, Linkage};
+use cranelift_module::{FuncId, Linkage, Module, Backend};
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap, error,
+	checked_if_let, checked_match, checked_unwrap_option, error,
 	frontend::syntax::{
 		BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration,
 		Declarator, DerivedDeclarator, DoWhileStatement, Expression, ExternalDeclaration,
@@ -25,7 +25,7 @@ use super::{
 	function::translate_function,
 	support::{
 		evaluate_constant_arithmetic_expression, AggregateIdentifier, AggregateType,
-		ConcreteModule, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer,
+		JitModule, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer,
 		PrimitiveIdentifier, SimpleType, SimpleTypedIdentifier, TypeBindingEnvironment,
 	},
 };
@@ -48,7 +48,7 @@ fn type_cast_value<'clif>(val: Value, ty: Type, func_builder: &'clif mut Functio
 
 fn translate_in_function_expression<'clif, 'tcx>(
 	expr: &'tcx Expression, type_hint: Option<Type>, func_builder: &'clif mut FunctionBuilder,
-	bm: &'clif mut ConcreteModule, name_env: &'_ NameBindingEnvironment<'tcx>,
+	bm: &'clif mut JitModule, name_env: &'_ NameBindingEnvironment<'tcx>,
 	type_env: &'_ TypeBindingEnvironment<'tcx>,
 ) -> Value {
 	use BinaryOperator::*;
@@ -79,7 +79,7 @@ fn translate_in_function_expression<'clif, 'tcx>(
 
 				PreIncrement => checked_if_let!(IdentifierExpr(var_name), operand.as_ref(), {
 					let var_name: &str = var_name.into();
-					let ident_var = checked_unwrap!(name_env.get(var_name));
+					let ident_var = checked_unwrap_option!(name_env.get(var_name));
 					checked_if_let!(
 						PrimitiveIdent(PrimitiveIdentifier { ident, ty: PrimitiveTy(ident_ty) }),
[…]

### 2020-01-08 src/frontend/semantics.rs

@@ -12,13 +12,13 @@ use std::{
 };
 
 use super::syntax::{
-	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator,
-	DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition,
-	Identifier, IfStatement, Integer, MemberExpression, MemberOperator, Statement, StructType,
-	TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator,
+	Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, Integer,
+	MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier, UnaryOperator,
+	UnaryOperatorExpression,
 };
 
-use crate::{checked_if_let, checked_match, checked_unwrap, error, unimpl};
+use crate::{checked_if_let, checked_match, checked_unwrap_option, error, unimpl};
 
 pub struct Environment<'a, K, Ty>
 where
@@ -118,10 +118,7 @@ where
 	T: 'a + Clone,
 {
 	pub fn new() -> Self {
-		Self {
-			env: HashMap::new(),
-			phantom: PhantomData,
-		}
+		Self { env: HashMap::new(), phantom: PhantomData }
 	}
 
 	pub fn inherit(&self) -> Self {
@@ -129,10 +126,7 @@ where
 		for (name, _) in &self.env {
 			inherited_env.get_mut(name).unwrap().rebind = false
 		}
-		Self {
-			env: inherited_env,
-			phantom: PhantomData,
-		}
+		Self { env: inherited_env, phantom: PhantomData }
 	}
 
 	pub fn bind(&mut self, name: K, ty: T) {
@@ -144,10 +138,7 @@ where
 	}
 
 	pub fn get(&self, name: K) -> &T {
-		self.env
-			.get(&name)
-			.map(|BoundedType { ty, .. }| ty)
-			.unwrap_or_else(|| error!("name not found in current scope"))
+		self.env.get(&name).map(|BoundedType { ty, .. }| ty).unwrap_or_else(|| error!("name not found in current scope"))
 	}
 }
 
@@ -220,9 +211,7 @@ impl<'a> SimpleType<'a> {
 	}
 
[…]

### 2020-01-08 src/helper.rs

@@ -13,10 +13,17 @@ macro_rules! unimpl {
 }
 
 #[macro_export]
-macro_rules! checked_unwrap {
+macro_rules! checked_unwrap_option {
 	($expr:expr) => {
 		$expr.unwrap_or_else(|| unsafe { unreachable_unchecked() })
-	};
+	}
+}
+
+#[macro_export]
+macro_rules! checked_unwrap_result {
+	($expr:expr) => {
+		$expr.unwrap_or_else(|_| unsafe { unreachable_unchecked() })
+	}
 }
 
 #[macro_export]

### 2020-01-08 src/main.rs

@@ -1,15 +1,26 @@
-use std::{fs, path::PathBuf};
-
-use zydis::{
-	AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer,
-	Signedness,
+use std::{
+	fs::{self, File},
+	hint::unreachable_unchecked,
+	mem,
+	path::PathBuf,
+	slice,
+	str::FromStr,
 };
+
+use cranelift::prelude::*;
+use cranelift_faerie::{FaerieBackend, FaerieBuilder, FaerieTrapCollection};
+use cranelift_simplejit::{SimpleJITBackend, SimpleJITBuilder};
+use target_lexicon::triple;
+
+use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
 
 use structopt::StructOpt;
 
 mod backend;
 mod frontend;
 mod helper;
+
+// use crate::{checked_unwrap_result};
 
 #[derive(StructOpt)]
 #[structopt(name = "tocc", about = "A type-obfuscated C compiler")]
@@ -20,55 +31,87 @@ struct Opt {
 
 	/// Function
 	#[structopt(name = "function", short = "f")]
-	fname: String,
+	fname: Option<String>,
+
+	/// JIT compilation
+	#[structopt(name = "code generation mode", short = "j")]
+	jit: bool,
 }
 
 fn main() {
 	let opt = Opt::from_args();
-	let (src, fname) = { (opt.src.as_path(), opt.fname.as_str()) };
+	// let (src, fname) = { (opt.src.as_path(), opt.fname.as_str()) };
+	let src = opt.src.as_path();
 
-	let src_code = fs::read_to_string(src).expect("Failed to read source code file");
+	let src_code = fs::read_to_string(src).expect("failed to read source code file");
 	let tu = frontend::syntax::parse(src_code.as_str());
 	frontend::semantics::check(&tu);
 
-	let mut am = backend::AbstractMachine::new(&tu);
-	if let Some(fptr) = am.compiled_function(fname) {
-		// println!("{}", &fclif);
+	if opt.jit {
+		let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
+		let mut am = backend::AbstractMachine::<'_, SimpleJITBackend>::new(&tu, builder);
+		if let Some(fname) = &opt.fname {
+			if let Some((fptr, flen)) = am.compiled_function(fname.as_str()) {
[…]

### 2020-01-21 paper/paper.tex
propagate original types

--- 2020-01-08 paper/paper.tex
@@
 to recover types of programs in Scheme - a dynamically typed language.
-Lee et al.~\cite{lee_tie_2011} introduces
-an extension for Mycroft's work which supports a limited form of subtyping.
+Lee et al.~\cite{lee_tie_2011} extend Mycroft's work by introducing a form of
+subtyping based on C's integer conversion rank, but lack of recursive type.
+Polymorphic Type Inference for Machine Code.
 Caballero and Lin give a survey~\cite{caballero_type_2016} for research up until 2015.
@@
 parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for related techniques.
-Type constraints are generated gradually through the \empĥ{low-level use} of objects.
+Type constraints are generated gradually through the \emph{low-level use} of objects.
 The system of constraints is solved then, each object is assigned a certain
@@
 
-\subsection{A Subsection Sample}
-Please note that the first paragraph of a section or subsection is
-not indented. The first paragraph that follows a table, figure,
-equation etc. does not need an indent, either.
+% \subsection{A Subsection Sample}
+% Please note that the first paragraph of a section or subsection is
+% not indented. The first paragraph that follows a table, figure,
+% equation etc. does not need an indent, either.
 
-Subsequent paragraphs, however, are indented.
+% Subsequent paragraphs, however, are indented.
 
-\subsubsection{Sample Heading (Third Level)} Only two levels of
-headings should be numbered. Lower level headings remain unnumbered;
-they are formatted as run-in headings.
+% \subsubsection{Sample Heading (Third Level)} Only two levels of
+% headings should be numbered. Lower level headings remain unnumbered;
+% they are formatted as run-in headings.
 
-\paragraph{Sample Heading (Fourth Level)}
-The contribution should contain no more than four levels of
-headings. Table~\ref{tab1} gives a summary of all heading levels.
+% \paragraph{Sample Heading (Fourth Level)}
+% The contribution should contain no more than four levels of
+% headings. Table~\ref{tab1} gives a summary of all heading levels.
 
-\begin{table}
-\caption{Table captions should be placed above the
-tables.}\label{tab1}
-\begin{tabular}{|l|l|l|}
-\hline
-Heading level &  Example & Font size and style\\
-\hline
-Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-\hline
-\end{tabular}
-\end{table}
+% \begin{table}
+% \caption{Table captions should be placed above the
+% tables.}\label{tab1}
+% \begin{tabular}{|l|l|l|}
+% \hline
+% Heading level &  Example & Font size and style\\
+% \hline
+% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
+% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
+% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
+% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
+% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
+% \hline
+% \end{tabular}
+% \end{table}
 
-\noindent Displayed equations are centered and set on a separate
-line.
-\begin{equation}
-x + y = z
-\end{equation}
-Please try to avoid rasterized images for line-art diagrams and
-schemas. Whenever possible, use vector graphics instead (see
-Fig.~\ref{fig1}).
+% \noindent Displayed equations are centered and set on a separate
+% line.
+% \begin{equation}
+% x + y = z
+% \end{equation}
+% Please try to avoid rasterized images for line-art diagrams and
+% schemas. Whenever possible, use vector graphics instead (see
+% Fig.~\ref{fig1}).
 
-\begin{figure}
-\includegraphics[width=\textwidth]{fig1.eps}
-\caption{A figure caption is always placed below the illustration.
-Please note that short captions are centered, while long ones are
-justified by the macro package automatically.} \label{fig1}
-\end{figure}
+% \begin{figure}
+% \includegraphics[width=\textwidth]{fig1.eps}
+% \caption{A figure caption is always placed below the illustration.
+% Please note that short captions are centered, while long ones are
+% justified by the macro package automatically.} \label{fig1}
+% \end{figure}
 
-\begin{theorem}
-This is a sample theorem. The run-in heading is set in bold, while
-the following text appears in italics. Definitions, lemmas,
-propositions, and corollaries are styled the same way.
-\end{theorem}
-%
-% the environments 'definition', 'lemma', 'proposition', 'corollary',
-% 'remark', and 'example' are defined in the LLNCS documentclass as well.
-%
-\begin{proof}
-Proofs, examples, and remarks have the initial word in italics,
-while the following text appears in normal font.
-\end{proof}
-For citations of references, we prefer the use of square brackets
-and consecutive numbers. Citations using labels or the author/year
-convention are also acceptable. The following bibliography provides
-a sample reference list with entries for journal
-articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-and a homepage~\cite{ref_url1}. Multiple citations are grouped
-\cite{ref_article1,ref_lncs1,ref_book1},
-\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
+% \begin{theorem}
+% This is a sample theorem. The run-in heading is set in bold, while
+% the following text appears in italics. Definitions, lemmas,
+% propositions, and corollaries are styled the same way.
+% \end{theorem}
+% %
+% % the environments 'definition', 'lemma', 'proposition', 'corollary',
+% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
+% %
+% \begin{proof}
+% Proofs, examples, and remarks have the initial word in italics,
+% while the following text appears in normal font.
+% \end{proof}
+% For citations of references, we prefer the use of square brackets
+% and consecutive numbers. Citations using labels or the author/year
+% convention are also acceptable. The following bibliography provides
+% a sample reference list with entries for journal
+% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
+% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
+% and a homepage~\cite{ref_url1}. Multiple citations are grouped
+% \cite{ref_article1,ref_lncs1,ref_book1},
+% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
 %

### 2020-01-21 paper/tool.tex
propagate original types

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[a4paper]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\usepackage[sorting=ynt,sortcites=true,backend=bibtex8,doi=false,maxnames=4,isbn=false,firstinits=true]{biblatex}
\addbibresource{reference}

\usepackage{hyperref}
\hypersetup
{
  bookmarks       = true,
  unicode         = true,
  pdftitle        = "Type Flattening Obfuscation",
  pdfauthor       = "Ta Thanh Dinh", %auteur du document
%   pdfsubject      = "A Conceptual Approach for Message Format Extraction",
  pdftoolbar      = true, %barre d'outils non visible
  pdfmenubar      = true, %barre de menu visible
  pdfhighlight    = /O, %effet d'un clic sur un lien hypertexte
  colorlinks      = true, %couleurs sur les liens hypertextes
%   pdfpagemode = None, %aucun mode de page
%   pdfpagelayout = SinglePage, %ouverture en simple page
  pdffitwindow    = true, %pages ouvertes entierement dans toute la fenetre
  linkcolor       = red, %couleur des liens hypertextes internes
  citecolor       = green, %couleur des liens pour les citations
  urlcolor        = cyan, %couleur des liens pour les url
%   pagebackref=true
%   bookmarksdepth  = 3
}

\usepackage{listings}
\lstset{basicstyle=\small\ttfamily,showspaces=false,frame=tb}
\lstloadlanguages{C,C++,[x86masm]Assembler}

\usepackage{cleveref}

\begin{document}
%
\title{Type Flattening Obfuscation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Ta Thanh Dinh}
%
\authorrunning{Ta Thanh Dinh}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
	\email{tathanhdinh@gmail.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
	Beside data and control flow, high-level types are also important in program analysis,
	indeed type reconstruction is an essential step in binary code decompilation.
	For the purpose of anti-decompilation, the paper introduces a novel obfuscation
	technique which makes types become harder to be reconstructed.

	% High-level type reconstruction is an important step in machine code decompilation.
	% Researchers show possibilities of mapping untyped machine-dependent
	% primitives into types of a C-like type system.

	% We show that the techniques used for type reconstruction can be bypassed,
	% and we claim that the bypass is always possible given \emph{semantics gap} between
	% type systems of high-level and machine language.
	% \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
An important step in binary code \emph{decompilation}~\cite{cifuentes_reverse_1994} is to detect high-level objects (e.g. functions,
variables) from low-level machine dependent objects~\cite{balakrishnan_divine_2007} (e.g. registers, raw memory accesses, machine
instructions) before annotate them with types of the supposed original language. Because
most of information about high-level types is lost in compilation, the binary code \emph{type reconstruction}
requires special techniques, a survey up until 2015 can be
referenced in~\cite{caballero_type_2016}.

In the opposite direction, binary code \emph{obfuscation} is to make
the decompilation (or in general code analysis) harder. Since the data and control flow are principal elements for the program analysis,
current obfuscation techniques~\cite{collberg_surreptitious_2009} focus mostly on hiding them.
But to the best of our knowledge, there is still no explicit effort in hiding high-level types.
There would be several reasons for this lack of effort.

\emph{First}, type obfuscation can be an indirect effect of data or control flow obfuscation.
Indeed, type reconstruction algorithms need both data and control flow to build type constraints,
if any of them is hidden
then the algorithms will not work. Or if the function boundary cannot be found
(because of anti-disassembing tricks, for example), then there are no inputs (i.e. high-level
objects) for type reconstruction. \emph{Second}, high-level types seem too coarse to be worthy
of being protected, in many cases just knowing certain values of the input which make the program
exploitable is enough. But knowledge about types enlarges attack surfaces because more analysis
can be proceeded, beside decompilation see the survey~\cite{caballero_type_2016} for a
more complete list.
% We exploit the \emph{semantics gap}

\section{Type flattening compiler}

We introduce \emph{ucc}, a proof-of-concept C compiler that explicitly obfuscates high-level types.
We attacks on the core of type reconstruction algorithms, that is the data flow used to build
type constraints, and the \emph{semantic gap} between types in the high-level language and their
representations in low-level machine code.

The compiler is open source and implemented in Rust. The source code, an user guide as well as some
demo results are available at (cite).

% \section{Introduction}
% Binary code type recovery is to restore high-level type information of variables,
% functions from machine codes. It is useful for reverse code engineering (e.g.
% decompilation) or static binary rewriting/instrumentation, just to name a few.
% Type recovery is available in several binary analysis
% tools~\cite{noauthor_hex-rays_nodate, noauthor_jeb_nodate, noauthor_ghidra_nodate}
% as a result of machine code decompilation. Academic research includes the classic
% paper of Mycroft~\cite{mycroft_type-based_1999} which is probably the first work
% on the domain, though earlier ideas~\cite{shivers_data-flow_1990} have been used
% to recover types of programs in Scheme - a dynamically typed language.
% Lee et al.~\cite{lee_tie_2011} extend Mycroft's work by introducing a form of
% subtyping based on C's integer conversion rank, but lack of recursive type.
% Polymorphic Type Inference for Machine Code.
% Caballero and Lin give a survey~\cite{caballero_type_2016} for research up until 2015.
% Recent directions are using machine learning~\cite{maier_typeminer_2019} or statistical
% language model~\cite{katz_estimating_2016}, which are out of scope of the paper.
% All approaches tend to output a C-like type system.

% Basically, the binary code type recovery starts by detecting high-level objects from
% machine-dependent primitives: local variables are stored in function stack frame,
% parameters are passed from registers, see~\cite{balakrishnan_wysinwyx_2007} for related techniques.
% Type constraints are generated gradually through the \emph{low-level use} of objects.
% The system of constraints is solved then, each object is assigned a certain
% (polymorphic) type.

% This bird view may give off an impression that the
% binary code type reconstruction is a well established research domain, incorrect results
% are because of foreign reasons: incorrect binary code disassembling,
% high-level variable detection, etc. But we claim that there are probably intrinsic problems.

% \emph{First}, there is a common agreement that type information is removed through
% compilation~\cite{lee_tie_2011,caballero_type_2016,lin_automatic_2010},
% but there is no explicit explication of why and how some type information is not needed,
% so removed, in machine codes. The result of reconstructing \emph{the most precise yet conservative}
% type~\cite{lee_tie_2011}, which may suggest the well-known
% \emph{principal types}~\cite{damas_principal_1982,hindley_principal_1969},
% is sound in a limited context only. Actually not all type
% information can be restored.

% \emph{Second}, though some techniques of data structure reverse
% engineering~\cite{caballero_type_2016, caballero_polyglot_2007} can be reused for
% type recovery, types do not always attach with storage specific primitives (for example
% \texttt{int} is some \texttt{32-bit} signed integer stored in a register or stack).
% The storage-based point of view is almost correct in low-level languages like C, it
% does not reveal the nature of types. In other languages, types can be
% zero-sized~\cite{noauthor_phantom_nodate}, another examples are
% \emph{regions}~\cite{grossman_region-based_2002} or \emph{units-of-measure}~\cite{kennedy_types_2010}
% which leave no storage imprint.

% \emph{Third}, current research uses some variants of
% \emph{Algorithm W}~\cite{milner_theory_1978,cardelli_basic_1987} to resolve type
% constraints in a C-like language. But the polymorphism in C is rather
% \emph{ad-hoc}~\cite{strachey_fundamental_2000}: some functions are
% trivially typed in C by casting, but not typeable in Hindley-Milner type system. This
% problem is remarked already in~\cite{mycroft_type-based_1999}, but unfortunately omitted in
% later extension~\cite{lee_tie_2011}. In real world, it is not rare to see type inconsistency in decompilation results
% of security tools.

% % used originally to
% % type check/inference for programs of Hindley-Milner's type system (abbr. HM).
% % While the supposed target is a C-like type system, some authors claim to replicate
% % the result of \emph{principal types}~\cite{damas_principal_1982,hindley_principal_1969}
% % by recovering \emph{the most precise yet conservative} type~\cite{lee_tie_2011}.
% % Such a result is sound in a limited context only, C's type system is not HM: there
% % are functions that are trivially typed in C by casting, but not typeable in HM's.
% % Actually, it is not rare to observe type inconsistency in decompilation results
% % of security tools.

% \paragraph{Contribution}
% We first discuss the type information loss in compilation and some cases
% where assigning a high-level \emph{type} for a low-level primitive
% is not possible. Though this part is not novel, we bring it to the context
% of binary code analysis to show limits of type reconstruction. Next, we present
% a proof-of-concept C compiler which tries to hide types from reconstruction techniques described
% in current researches.

% \section{Type information loss}
% Informally speaking, a type system is some set of constraints and rules to infer constraints
% on a program. The type system decides which are allowed or forbidden on the semantics of the language,
% for example adding two pointers is not allowed in C because this operation is semantically nonsense.
% Type helps avoid bugs as summarized in Milner's famous
% slogan~\textquote{well-type program cannot go wrong}~\cite{milner_theory_1978}.

% In statically typed languages, the compiler checks the type constraints then generates
% machine codes (we consider here only languages which generates machine codes), but then
% most of constraints are lost because they are not needed for running
% the program. There are at least two sources of
% information loss: \emph{type erasure} and \emph{data indistinguishability},
% happening at different phases of compilation.

% \subsection{Type erasure}
% \emph{Type erasure} means the "intensional" type of an object is hidden/inaccessible or
% completely removed in some context. It appears under several concepts: subtype substitution,
% generic specialization (or monomorphization), or boxing, just name a few. In some cases,
% e.g. subtype substitution, the (sub)type of the wrapped object does not completely removed,
% it is just not accessible in contexts where only behaviors of the super type are allowed.
% Such a case will not be discussed in the paper since we look at the low-level machine code.

% Once the program is type checked,
% % the type information is normally not needed for evaluation (i.e. running program),
% the compiler will select a consistent machine-dependent
% representation for each high-level type, this representation may only have little
% relation with the original type but it does not violate the fact that the program
% is checked, then safe.

% \begin{example}\label{exa:typed_enum}
% 	\texttt{C++}'s typed enum.

% 	\begin{lstlisting}[frame=lines, language={C++}]
% enum E { one = 1, two };
% void foo(enum E e) {
%   switch (e) {
%   case E::one:
%   case E::two:
%     printf("ok\n");
%     break;

%   default: assert(false);
%   }
% }

% enum E bar() {...return some enum E }

% int main() {
%   enum E e = bar(); foo(e);
%   return 0:
% }
% \end{lstlisting}

% 	The program is safe when type-checked: \texttt{assert(0)} will
% 	never be reached when the program runs. In machine code, we may observe that
% 	\texttt{foo} is a function accepting a \texttt{32-bit} signed integer, i.e. information about
% 	\texttt{enum E} type is erased. However there is no need to add runtime
% 	checking for the case where \texttt{foo} is passed an argument of value not in \texttt{enum E}
% 	(e.g. \texttt{3}), this case is eliminated by the compiler's type checker.
% \end{example}

% \subsection{Data indistinguishability}
% When generating binary code for a specific hardware/operating system, the compiler will
% use a consistent representation for low-level primitives (e.g. registers used in
% function parameters or return value, alignment for fields of aggregate types), so that
% the output binary can be used by other programs on the same system. It it possible that
% two types are distinguished at high-level but they have the same data representation
% at low-level.

% \begin{example}\label{exa:register_struct}
% 	Small struct passing.

% 	\begin{lstlisting}[frame=lines, language={C}]
% struct S { int a; int b; };
% int foo(struct S s) {
%   return s.a + s.b;
% }

% int bar(long long l) {
%   return (int)l + (int)(l >> 32);
% }
% \end{lstlisting}

% 	Under System V AMD64 ABI~\cite{lu_system_nodate}, the aggregate type \texttt{S}
% 	has class \texttt{INTEGER}: the argument \texttt{s} is passed just in register \texttt{rdi}.
% 	At the ABI level, \texttt{foo} and \texttt{bar} is interchangeable, but they are not at
% 	the type level.
% \end{example}

% \subsection{Untypeable}

% There is no type casting in Hindley-Milner's type system (abbr. HM), so when using a variant of
% \emph{Algorithm-W}~\cite{milner_theory_1978} for binary code type inference, the output (as a
% C program without type casting) may not exist: there are programs which are
% trivially typed in C, but not in HM.

% \begin{example}\label{exa:untypeable}
% 	Untypeable function.
% 	\begin{lstlisting}[frame=topline, language={C}]
% int foo(int i, int *f) {
%   return ((int (*)(int (*)(int, int*), int))f)(foo, i);
% }
% \end{lstlisting}
% 	Disassembled code:
% 	\begin{lstlisting}[frame=bottomline, language={[x86masm]Assembler}]
% 0x0     55                               push rbp
% 0x1     48 89 e5                         mov rbp, rsp
% 0x4     48 83 ec 10                      sub rsp, 0x10
% 0x8     89 7d fc                         mov [rbp-0x4], edi
% 0xb     48 89 75 f0                      mov [rbp-0x10], rsi
% 0xf     48 8b 45 f0                      mov rax, [rbp-0x10]
% 0x13    8b 75 fc                         mov esi, [rbp-0x4]
% 0x16    48 bf 00 00 00 00 00 00 00 00    mov rdi, 0x0
% 0x20    ff d0                            call rax
% 0x22    48 83 c4 10                      add rsp, 0x10
% 0x26    5d                               pop rbp
% 0x27    c3                               ret
% \end{lstlisting}

% 	From disassembled code, it is direct to detect that the second argument
% 	of \texttt{foo} is of functional type (since \texttt{call rax} at address \texttt{0x20}),
% 	but assigning an functional type for \texttt{f} is not possible.
% \end{example}

% The inevitability of type information loss means that the binary code
% type reconstruction cannot always reaches the notion of
% \emph{the most precise yet conservative type}~\cite{lee_tie_2011}. Since
% compilation is a \textquote{many-to-one mapping}~\cite{mycroft_type-based_1999},
% real world decompilers simply look for one of possible maps,
% sometimes they accept even inconsistencies in reconstructed types.

% \section{Untyped C}

% \emph{well-type program cannot go wrong}, or even leads to better optimization.

% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.

% Subsequent paragraphs, however, are indented.

% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.

% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.

% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}

% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\printbibliography
\end{document}

### 2020-01-21 src/backend/function.rs

@@ -14,34 +14,32 @@ use cranelift_codegen::{
 	},
 	Context,
 };
-use cranelift_module::{Backend, FuncId, Linkage, Module};
+use cranelift_module::{Backend, FuncId, Module};
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap_option, checked_unwrap_result,
+	checked_if_let, checked_match, checked_unwrap_option,
 	frontend::syntax::{
-		BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration,
-		Declarator, DerivedDeclarator, DoWhileStatement, Expression, ExternalDeclaration,
-		ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, Integer,
-		MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier,
-		UnaryOperator, UnaryOperatorExpression, WhileStatement,
+		BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator,
+		DoWhileStatement, Expression, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement,
+		MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+		WhileStatement,
 	},
 	generate_random_maps, unimpl,
 };
 
 use super::support::{
-	evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier,
-	AggregateType, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer,
-	PrimitiveIdentifier, SimpleConcreteType, SimpleType, SimpleTypedIdentifier,
-	TypeBindingEnvironment,
+	evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue,
+	EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier,
+	SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment,
 };
 
 static NEW_VAR_ID: AtomicUsize = AtomicUsize::new(0);
 
[…]

### 2020-01-21 src/backend/support.rs

@@ -18,11 +18,18 @@ use crate::{
 	},
 };
 
-pub enum SimpleConcreteType {
+#[derive(Debug)]
+pub enum ConcreteValue {
 	ConstantTy(i64),
 	ValueTy(Value),
 	StackSlotTy(StackSlot),
-	UnitTy,
+	Unit,
+}
+
+#[derive(Debug)]
+pub struct SimpleTypedConcreteValue<'a> {
+	pub ty: EffectiveType<'a>,
+	pub val: ConcreteValue,
 }
 // EaC 7.7.1 Understanding Structure Layout
 // DRAGON 6.3.4 Storage Layouts for Local Names
@@ -78,35 +85,36 @@ pub struct FunctionType {
 }
 
 #[derive(Clone, Debug)]
-pub enum SimpleType<'a> {
+pub enum EffectiveType<'a> {
 	PrimitiveTy(Type),
 	AggregateTy(AggregateType<'a>),
 	FunctionTy(FunctionType),
-	PointerTy(Box<SimpleType<'a>>),
+	PointerTy(Box<EffectiveType<'a>>),
+	UnitTy,
 }
 
 #[derive(Clone, Debug)]
 pub struct PrimitiveIdentifier<'a> {
 	pub ident: Variable,
-	pub ty: SimpleType<'a>,
+	pub ty: EffectiveType<'a>,
 }
 
 #[derive(Clone, Debug)]
 pub struct FunctionIdentifier<'a> {
 	pub ident: FuncId,
-	pub ty: SimpleType<'a>,
+	pub ty: EffectiveType<'a>,
 }
 
 #[derive(Clone, Debug)]
 pub struct AggregateIdentifier<'a> {
 	pub ident: StackSlot,
-	pub ty: SimpleType<'a>,
+	pub ty: EffectiveType<'a>,
 }
 
 #[derive(Clone, Debug)]
 pub struct PointerIdentifer<'a> {
 	pub ident: Variable,
-	pub ty: SimpleType<'a>,
+	pub ty: EffectiveType<'a>,
 }
 
 #[derive(Clone, Debug)]
@@ -135,7 +143,7 @@ impl Into<Type> for &TypeSpecifier<'_> {
 pub type NameBindingEnvironment<'a> = Environment<'a, &'a str, SimpleTypedIdentifier<'a>>;
 
 // visible types
-pub type TypeBindingEnvironment<'a> = HashMap<&'a str, SimpleType<'a>>;
[…]

### 2020-01-21 src/backend/translation.rs

@@ -13,7 +13,7 @@ use crate::{
 use super::{
 	function::{blur_function_signature, get_function_signature, translate_function},
 	support::{
-		AggregateType, FunctionIdentifier, FunctionType, NameBindingEnvironment, SimpleType,
+		AggregateType, FunctionIdentifier, FunctionType, NameBindingEnvironment, EffectiveType,
 		SimpleTypedIdentifier, TypeBindingEnvironment,
 	},
 };
@@ -53,7 +53,7 @@ pub fn compile<'clif, 'tcx>(
 					fname,
 					SimpleTypedIdentifier::FunctionIdent(FunctionIdentifier {
 						ident: func_id,
-						ty: SimpleType::FunctionTy(FunctionType {
+						ty: EffectiveType::FunctionTy(FunctionType {
 							return_ty,
 							param_ty: param_ty.clone(),
 						}),
@@ -72,7 +72,7 @@ pub fn compile<'clif, 'tcx>(
 				checked_match!(specifier, StructTy(struct_ty), {
 					let StructType { identifier: Identifier(sname), .. } = struct_ty;
 					let aggre_ty: AggregateType = struct_ty.into();
-					type_env.insert(sname, SimpleType::AggregateTy(aggre_ty))
+					type_env.insert(sname, EffectiveType::AggregateTy(aggre_ty))
 				});
 			}
 		}

### 2020-01-21 src/frontend/semantics.rs

@@ -1,24 +1,18 @@
 // semantics analysis
 
 use std::{
-	borrow::Borrow,
-	cmp,
-	collections::{HashMap, HashSet},
-	hash::Hash,
-	hint::unreachable_unchecked,
-	i16, i32, i64, i8,
-	marker::PhantomData,
-	sync::atomic::{AtomicUsize, Ordering},
+	borrow::Borrow, cmp, collections::HashMap, hash::Hash, hint::unreachable_unchecked, i16, i32,
+	i64, i8, marker::PhantomData, sync::atomic::AtomicUsize,
 };
 
 use super::syntax::{
 	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator,
 	DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition,
-	Identifier, IfStatement, Integer, MemberExpression, MemberOperator, Statement, StructType,
+	Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType,
 	TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
 };
 
-use crate::{checked_if_let, checked_match, checked_unwrap_option, error, unimpl};
+use crate::{checked_match, checked_unwrap_option, error, unimpl};
 
 #[derive(Clone, Debug)]
 pub struct Environment<'a, K, Ty>
@@ -334,8 +328,19 @@ impl<'a> SimpleType<'a> {
 							IdentifierExpr(_) | MemberExpr(_) => {}
 							_ => error!("expression is not a lvalue"),
 						}
-						Self::PointerTy(Box::new(operand_ty))
+						PointerTy(Box::new(operand_ty))
 					}
+
+					Indirection => match &operand_ty {
+						PointerTy(ty) => match ty.as_ref() {
+							FunctionTy(_) => error!("unable to dereference function pointer"),
+							PointerTy(_) => todo!(),
+							UnitTy => error!("unable to dereference unit pointer"),
+							_ => ty.as_ref().to_owned(),
+						},
+
+						_ => error!("dereferene a non-pointer type"),
+					},
 				}
 			}
 
@@ -347,35 +352,58 @@ impl<'a> SimpleType<'a> {
 				}
 
 				match operator {
-					Multiplication | Division | Remainder | Addition | Subtraction => {
[…]

### 2020-01-21 src/frontend/syntax.rs

@@ -7,21 +7,22 @@ const KEYWORDS: &'_ [&'_ str] = &[
 	"if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void",
 ];
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub enum UnaryOperator {
 	Negation,
 	PostIncrement,
 	PreIncrement,
 	Address,
+	Indirection,
 }
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub struct UnaryOperatorExpression<'a> {
 	pub operator: UnaryOperator,
 	pub operand: Box<Expression<'a>>,
 }
 
-#[derive(Clone, PartialEq, Eq)]
+#[derive(Clone, Debug, PartialEq, Eq)]
 pub enum BinaryOperator {
 	Multiplication,
 	Division,
@@ -33,6 +34,7 @@ pub enum BinaryOperator {
 	Greater,
 	GreaterOrEqual,
 	Equal,
+	NotEqual,
 	Assignment,
 	AdditionAssignment,
 	SubtractionAssignment,
@@ -40,13 +42,13 @@ pub enum BinaryOperator {
 	DivisionAssignment,
 }
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub enum MemberOperator {
 	Direct,
 	Indirect,
 }
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub struct Integer(pub i64);
 
 impl Into<i64> for &'_ Integer {
@@ -61,19 +63,19 @@ impl Into<i64> for Integer {
 	}
 }
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub enum Constant {
 	IntegerConst(Integer),
 }
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub struct BinaryOperatorExpression<'a> {
 	pub operator: BinaryOperator,
 	pub lhs: Box<Expression<'a>>,
 	pub rhs: Box<Expression<'a>>,
 }
 
-#[derive(Clone)]
+#[derive(Clone, Debug)]
 pub struct MemberExpression<'a> {
 	pub operator: MemberOperator,
 	pub expression: Box<Expression<'a>>,
@@ -81,13 +83,13 @@ pub struct MemberExpression<'a> {
 }
 
 // Simplified function calls (C11 6.5.5.2 Function calls)
-#[derive(Clone)]
+#[derive(Clone, Debug)]
[…]

### 2020-01-21 src/helper.rs

@@ -29,11 +29,7 @@ macro_rules! checked_unwrap_result {
 #[macro_export]
 macro_rules! checked_if_let {
 	($pat:pat, $expr:expr, $block:block) => {
-		if let $pat = $expr {
-			$block
-		} else {
-			unsafe { unreachable_unchecked() }
-			}
+		if let $pat = $expr { $block } else { unsafe { unreachable_unchecked() } }
 	};
 }
 

### 2020-01-21 src/main.rs

@@ -256,4 +256,19 @@ mod tests {
 	fn compile_16() {
 		assert_eq!(compile_and_run_int_to_int("tests/16.c", "foo", 0), 4);
 	}
+
+	#[test]
+	fn compile_17() {
+		assert_eq!(compile_and_run_int_to_int("tests/17.c", "fibo", 6), 8);
+	}
+
+	#[test]
+	fn compile_18() {
+		assert_eq!(compile_and_run_int_to_int("tests/18.c", "sum_0n", 4), 10);
+	}
+
+	#[test]
+	fn compile_19() {
+		assert_eq!(compile_and_run_int_to_int("tests/19.c", "collatz", 5), 4);
+	}
 }

### 2020-01-21 tests/17.c

@@ -1,0 +1,13 @@
+int fibo(int n) {
+	int result;
+	if (n <= 0) {
+		result = 0;
+	} else {
+		if (n == 1) {
+			result = 1;
+		} else {
+			result = fibo(n - 1) + fibo(n - 2);
+		}
+	}
+	return result;
+}

### 2020-01-21 tests/18.c

@@ -1,0 +1,12 @@
+int sum_0n(int n) {
+	int result;
+	if (n <= 0) {
+		result = 0;
+	} else {
+		int i;
+		for (i = 0; i <= n; i++) {
+			result += i;
+		}
+	}
+	return result;
+}

### 2020-01-21 tests/19.c

@@ -1,0 +1,15 @@
+int collatz(int n) {
+	int next;
+	if (n % 2 == 0) {
+		next = n / 2;
+	} else {
+		next = 3 * n + 1;
+	}
+	int result;
+	if (next == 1) {
+		result = 0;
+	} else {
+		result = collatz(next) + 1;
+	}
+	return result;
+}

### 2020-01-21 tests/20.c

@@ -1,0 +1,9 @@
+int foo(int x, int y) {
+	int result;
+	if (x > y) {
+		return 1;
+	} else {
+		return 0;
+	}
+	return -1;
+}

### 2020-01-21 tests/21.c

@@ -1,0 +1,7 @@
+int slen(char *s) {
+	int len = 0;
+	while (*s != 0) {
+		s++; len++;
+	}
+	return len;
+}

### 2020-01-24 paper/tool.tex
implement type equivalence

@@
 
-\usepackage{cleveref}
+% \usepackage{cleveref}
+% \usepackage{adjustbox}
+\usepackage[strict]{changepage}
 
@@
 \section{Introduction}
-An important step in binary code \emph{decompilation}~\cite{cifuentes_reverse_1994} is to detect high-level objects (e.g. functions,
-variables) from low-level machine dependent objects~\cite{balakrishnan_divine_2007} (e.g. registers, raw memory accesses, machine
+An important step in binary code \emph{decompilation}~\cite{cifuentes_reverse_1994} is to
+detect high-level objects (e.g. functions, variables) from low-level machine dependent
+objects~\cite{balakrishnan_divine_2007} (e.g. registers, raw memory accesses, machine
 instructions) before annotate them with types of the supposed original language. Because
-most of information about high-level types is lost in compilation, the binary code \emph{type reconstruction}
-requires special techniques, a survey up until 2015 can be
+most of information about high-level types is lost in compilation, the binary code
+\emph{type reconstruction} requires special techniques, a survey up until 2015 can be
 referenced in~\cite{caballero_type_2016}.
 
-In the opposite direction, binary code \emph{obfuscation} is to make
-the decompilation (or in general code analysis) harder. Since the data and control flow are principal elements for the program analysis,
-current obfuscation techniques~\cite{collberg_surreptitious_2009} focus mostly on hiding them.
-But to the best of our knowledge, there is still no explicit effort in hiding high-level types.
-There would be several reasons for this lack of effort.
+In the opposite direction, binary code \emph{obfuscation} is to make the decompilation (or in
+general code analysis) harder. Since the data and control flow are principal elements for the
+program analysis, current obfuscation techniques~\cite{collberg_surreptitious_2009} focus mostly
+on hiding them. But to the best of our knowledge, there is still no explicit effort in hiding
+high-level types. There would be several reasons for this lack of effort.
 
-\emph{First}, type obfuscation can be an indirect effect of data or control flow obfuscation.
+\emph{First}, type obfuscation can be obtained as side effects of data or control flow obfuscation.
 Indeed, type reconstruction algorithms need both data and control flow to build type constraints,
 if any of them is hidden
-then the algorithms will not work. Or if the function boundary cannot be found
+then the algorithms cannot work correctly. Or if the function boundary cannot be found
 (because of anti-disassembing tricks, for example), then there are no inputs (i.e. high-level
@@
 of being protected, in many cases just knowing certain values of the input which make the program
-exploitable is enough. But knowledge about types enlarges attack surfaces because more analysis
+exploitable is enough. But knowledge about types expands attack surfaces because more analysis
 can be proceeded, beside decompilation see the survey~\cite{caballero_type_2016} for a
@@
 \section{Type flattening compiler}
+We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types.
+Our effort is to attack the core of type reconstruction algorithms,
+that is the data flow used to build type constraints, and the \emph{semantic gap} between types in the high-level language and their
+representations in low-level machine code. For that purpose, \emph{uCc} uses extensively
+obfuscation transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
+To increase code diversity, it is a \emph{probabilistic} compiler: given the source
+code, \emph{uCc} generates each time a different (but computationally equivalent) output machine code.
 
-We introduce \emph{ucc}, a proof-of-concept C compiler that explicitly obfuscates high-level types.
-We attacks on the core of type reconstruction algorithms, that is the data flow used to build
-type constraints, and the \emph{semantic gap} between types in the high-level language and their
-representations in low-level machine code.
+The compiler is implemented in Rust, uses \emph{cranelift}~\cite{noauthor_cranelift_nodate} as
+backend. The source code and a short user guide are at (cite). We test outputs of
+\emph{uCc} against decent decompilers, table~\ref{flattening} show experimental results
 
-The compiler is open source and implemented in Rust. The source code, an user guide as well as some
-demo results are available at (cite).
+\begin{table}
+	\begin{center}
+		\caption{Functions and original types}
+		\begin{tabular}{|l|l|}
+			\hline
+			Description & Function type \\
+			\hline
+			identity & \texttt{int id(int)} \\
+			\hline
+			division & \texttt{int div(short, char)} \\
+			\hline
+			modular & \texttt{int mod(int)} \\
+			\hline
+			increase pointer then dereference & \texttt{int inc\_deref(int*)} \\
+			\hline
+		\end{tabular}
+	\end{center}
+\end{table}
+
+\begin{table}
+	\begin{adjustwidth}{-6.21in}{-5.95in}
+		\begin{center}
+			% \centering
+			\caption{Type flattening effect}\label{flattening}
+			% \begin{adjustbox}{max width=1.5\textwidth}
+			\begin{tabular}{|l|l|l|l|l|}
+				\hline
+				Original type & Hex-Rays & JEB & Ghidra & Snowman \\
+				\hline
+				\texttt{int id(int)} & \texttt{int64 id(int64)} & \texttt{ulong id(ulong)} &
+				\texttt{ulong id(void)} & \texttt{int64 id(int64)} \\
+				\hline
+				\texttt{short div(short, char)} & \texttt{int64 div(uint64, uint64)} & \texttt{div\_t div(int, int)} &
+				\texttt{div\_t div(int, int)} & \texttt{int64\_t div(int64, int64)} \\
+				\hline
+				\texttt{char mod(short, char)} & \texttt{int64 mod(int64, int64)} & \texttt{ulong mod(ulong, ulong)} &
+				\texttt{ulong mod(void)} & \texttt{int64 mod(int64, int64)} \\
+				\hline
+				\texttt{int inc\_deref(int*)} & \texttt{int64 inc\_deref(int64)} & \texttt{ulong inc\_deref(ulong)} &
+				\texttt{ulong inc\_deref(undefined8)} & \texttt{int64 inc\_deref(uint64)} \\
+				\hline
+			\end{tabular}
+		\end{center}
+	\end{adjustwidth}
+\end{table}
+
+% \begin{table}
+% \caption{Table captions should be placed above the
+% tables.}\label{tab1}
+% \begin{tabular}{|l|l|l|}
+% \hline
+% Heading level &  Example & Font size and style\\
+% \hline
+% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
+% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
+% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
+% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
+% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
+% \hline
+% \end{tabular}
+% \end{table}
 

### 2020-01-24 demo/add.c

@@ -1,0 +1,3 @@
+short add(short x, short y) {
+	return x + y;
+}

### 2020-01-24 demo/collatz.c

@@ -1,0 +1,13 @@
+int collatz(int n) {
+	int next = 3 * n + 1;
+	if (n % 2 == 0) {
+		next = n / 2;
+	}
+
+	if (next == 1) {
+		return 1;
+	} else {
+		return collatz(next) + 1;
+	}
+	return 0;
+}

### 2020-01-24 demo/deref.c

@@ -1,0 +1,5 @@
+int inc_deref(int *x) {
+	int *p = x;
+	p += 1;
+	return *p;
+}

### 2020-01-24 demo/div.c

@@ -1,0 +1,3 @@
+short div(short x, char y) {
+	return x / y;
+}

### 2020-01-24 demo/fibo.c

@@ -1,0 +1,13 @@
+int fibo(int n) {
+	if (n <= 0) {
+		return 0;
+	} else {
+		if (n == 1) {
+			return 1;
+		}
+		else {
+			return fibo(n - 1) + fibo(n - 2);
+		}
+	}
+	return 0;
+}

### 2020-01-24 demo/id.c

@@ -1,0 +1,3 @@
+int id(int x) {
+	return x;
+}

### 2020-01-24 demo/mod.c

@@ -1,0 +1,3 @@
+char mod(short x, char y) {
+	return x % y;
+}

### 2020-01-24 demo/slen.c

@@ -1,0 +1,8 @@
+int slen(char *s) {
+	int len = 0;
+	while (*s != 0) {
+		s++;
+		len++;
+	}
+	return len;
+}

### 2020-01-24 demo/sum.c

@@ -1,0 +1,10 @@
+int sum(short *a, int n) {
+	int sum = 0;
+	int i = 0;
+	int *a_i;
+	for (; i < n; i++) {
+		a_i = a + i;
+		sum += *a_i;
+	}
+	return sum;
+}

### 2020-01-24 src/backend.rs

@@ -9,9 +9,7 @@ mod support;
 mod translation;
 
 use crate::frontend::syntax::TranslationUnit;
-use support::{
-	FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment,
-};
+use support::{FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment};
 
 // an abstract machine that runs Cranelift IR
 pub struct AbstractMachine<'s, B: Backend> {
@@ -43,7 +41,5 @@ impl<'s, B: Backend> AbstractMachine<'s, B> {
 		}
 	}
 
-	pub fn finish(self) -> B::Product {
-		self.module.finish()
-	}
+	pub fn finish(self) -> B::Product { self.module.finish() }
 }

### 2020-01-24 src/backend/function.rs

@@ -19,18 +19,16 @@ use cranelift_module::{Backend, FuncId, Module};
 use crate::{
 	checked_if_let, checked_match, checked_unwrap_option,
 	frontend::syntax::{
-		BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator,
-		DoWhileStatement, Expression, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement,
-		MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+		BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator,
+		FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
 		WhileStatement,
 	},
-	generate_random_maps, unimpl,
+	generate_random_maps, semantically_unreachable, unimpl,
 };
 
 use super::support::{
-	evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue,
-	EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier,
-	SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment,
+	evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue, EffectiveType, FunctionIdentifier, FunctionType,
+	NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment,
 };
 
 static NEW_VAR_ID: AtomicUsize = AtomicUsize::new(0);
@@ -239,8 +237,8 @@ fn create_entry_ebb(fb: &'_ mut FunctionBuilder, param_ty: &[Type], pointer_ty: 
 }
 
 fn declare_parameter_variables<'tcx>(
-	func_def: &'_ FunctionDefinition<'tcx>, fb: &'_ mut FunctionBuilder, entry_ebb: Ebb, pointer_ty: Type,
[…]

### 2020-01-24 src/backend/support.rs

@@ -11,9 +11,8 @@ use crate::{
 	frontend::{
 		semantics::Environment,
 		syntax::{
-			BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator,
-			Expression, Identifier, StructType, TypeSpecifier, UnaryOperator,
-			UnaryOperatorExpression,
+			BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression, Identifier, StructType, TypeSpecifier,
+			UnaryOperator, UnaryOperatorExpression,
 		},
 	},
 };
@@ -22,6 +21,7 @@ use crate::{
 pub enum ConcreteValue {
 	ConstantTy(i64),
 	ValueTy(Value),
+	#[allow(unused)]
 	StackSlotTy(StackSlot),
 	Unit,
 }
@@ -33,7 +33,7 @@ pub struct SimpleTypedConcreteValue<'a> {
 }
 // EaC 7.7.1 Understanding Structure Layout
 // DRAGON 6.3.4 Storage Layouts for Local Names
-#[derive(Clone, Debug)]
+#[derive(Clone, Debug, PartialEq, Eq)]
 pub struct AggregateType<'a> {
 	pub fields: Vec<(&'a str, Type)>,
 }
@@ -56,9 +56,7 @@ impl AggregateType<'_> {
 		Some(*fty)
 	}
 
-	pub fn bytes(&self) -> usize {
-		self.fields.iter().fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize)
-	}
+	pub fn bytes(&self) -> usize { self.fields.iter().fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize) }
 }
 
 impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
@@ -69,22 +67,20 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 		let fields: Vec<(&str, Type)> = declarations
 			.iter()
 			.map(|Declaration { specifier, declarator }| {
-				checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, {
-					(*ident, specifier.into())
-				})
+				checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, { (*ident, specifier.into()) })
 			})
 			.collect();
 		AggregateType { fields }
 	}
 }
 
-#[derive(Clone, Debug)]
[…]

### 2020-01-24 src/backend/translation.rs

@@ -4,23 +4,17 @@ use cranelift_module::{Backend, FuncId, Linkage, Module};
 
 use crate::{
 	checked_match, checked_unwrap_result,
-	frontend::syntax::{
-		Declaration, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier,
-		StructType, TranslationUnit, TypeSpecifier,
-	},
+	frontend::syntax::{Declaration, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier, StructType, TranslationUnit, TypeSpecifier},
+	semantically_unreachable,
 };
 
 use super::{
 	function::{blur_function_signature, get_function_signature, translate_function},
-	support::{
-		AggregateType, FunctionIdentifier, FunctionType, NameBindingEnvironment, EffectiveType,
-		SimpleTypedIdentifier, TypeBindingEnvironment,
-	},
+	support::{AggregateType, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment},
 };
 
 pub fn compile<'clif, 'tcx>(
-	tu: &'tcx TranslationUnit, module: &'clif mut Module<impl Backend>,
-	name_env: &'_ mut NameBindingEnvironment<'tcx>, type_env: &'_ mut TypeBindingEnvironment<'tcx>,
+	tu: &'tcx TranslationUnit, module: &'clif mut Module<impl Backend>, name_env: &'_ mut NameBindingEnvironment<'tcx>, type_env: &'_ mut TypeBindingEnvironment<'tcx>,
 ) -> Vec<(FuncId, usize)> {
 	use ExternalDeclaration::*;
 	use TypeSpecifier::*;
@@ -35,35 +29,22 @@ pub fn compile<'clif, 'tcx>(
 	for dec in extern_decs {
 		match dec {
 			FunctionDefinitionDecl(func_def) => {
-				let FunctionDefinition {
-					declarator: FunctionDeclarator { identifier: Identifier(fname), .. },
-					..
-				} = func_def;
+				let FunctionDefinition { declarator: FunctionDeclarator { identifier: Identifier(fname), .. }, .. } = func_def;
 
 				let (return_ty, param_ty) = get_function_signature(func_def, pointer_ty);
 				blur_function_signature(return_ty, &param_ty, pointer_ty, &mut ctxt);
 
-				let func_id = checked_unwrap_result!(module.declare_function(
-					fname,
[…]

### 2020-01-24 src/frontend/semantics.rs

@@ -1,18 +1,14 @@
 // semantics analysis
 
-use std::{
-	borrow::Borrow, cmp, collections::HashMap, hash::Hash, hint::unreachable_unchecked, i16, i32,
-	i64, i8, marker::PhantomData, sync::atomic::AtomicUsize,
-};
+use std::{borrow::Borrow, cmp, collections::HashMap, hash::Hash, hint::unreachable_unchecked, i16, i32, i64, i8, marker::PhantomData};
 
 use super::syntax::{
-	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator,
-	DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition,
-	Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType,
-	TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator,
+	FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier, UnaryOperator,
+	UnaryOperatorExpression,
 };
 
-use crate::{checked_match, checked_unwrap_option, error, unimpl};
+use crate::{checked_match, checked_unwrap_option, error, semantically_unreachable, unimpl};
 
 #[derive(Clone, Debug)]
 pub struct Environment<'a, K, Ty>
@@ -30,81 +26,55 @@ pub struct IdentifierName<'a>(&'a str);
 pub struct TypeName<'a>(&'a str);
 
 impl Borrow<str> for &'_ IdentifierName<'_> {
-	fn borrow(&self) -> &str {
-		self.0
-	}
+	fn borrow(&self) -> &str { self.0 }
 }
 
 impl Borrow<str> for &'_ TypeName<'_> {
-	fn borrow(&self) -> &str {
-		self.0
-	}
+	fn borrow(&self) -> &str { self.0 }
 }
 
 impl<'a> From<&'a str> for IdentifierName<'a> {
-	fn from(i: &'a str) -> Self {
-		IdentifierName(i)
-	}
[…]

### 2020-01-24 src/frontend/syntax.rs

@@ -3,9 +3,7 @@ use std::hint::unreachable_unchecked;
 
 use crate::error;
 
-const KEYWORDS: &'_ [&'_ str] = &[
-	"if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void",
-];
+const KEYWORDS: &'_ [&'_ str] = &["if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void"];
 
 #[derive(Clone, Debug)]
 pub enum UnaryOperator {
@@ -40,6 +38,9 @@ pub enum BinaryOperator {
 	SubtractionAssignment,
 	MultiplicationAssignment,
 	DivisionAssignment,
+	BitwiseAnd,
+	BitwiseXor,
+	BitwiseOr,
 }
 
 #[derive(Clone, Debug)]
@@ -52,15 +53,11 @@ pub enum MemberOperator {
 pub struct Integer(pub i64);
 
 impl Into<i64> for &'_ Integer {
-	fn into(self) -> i64 {
-		self.0
-	}
+	fn into(self) -> i64 { self.0 }
 }
 
 impl Into<i64> for Integer {
-	fn into(self) -> i64 {
-		self.0
-	}
+	fn into(self) -> i64 { self.0 }
 }
 
 #[derive(Clone, Debug)]
@@ -305,6 +302,28 @@ peg::parser! {grammar parser() for str {
 				operator: BinaryOperator::DivisionAssignment,
 				lhs: Box::new(a),
 				rhs: Box::new(b),
+			})
+		}
+		--
+		a:(@) blank()* "&" blank()* b:@ {
+			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
+				operator: BinaryOperator::BitwiseAnd,
+				lhs: Box::new(a),
+				rhs: Box::new(b)
+			})
+		}
+		a:(@) blank()* "^" blank()* b:@ {
+			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
+				operator: BinaryOperator::BitwiseXor,
+				lhs: Box::new(a),
+				rhs: Box::new(b)
+			})
+		}
+		a:(@) blank()* "|" blank()* b:@ {
+			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
+				operator: BinaryOperator::BitwiseOr,
+				lhs: Box::new(a),
+				rhs: Box::new(b)
 			})
 		}
 		--
@@ -627,11 +646,7 @@ peg::parser! {grammar parser() for str {
[…]

### 2020-01-24 src/helper.rs

@@ -13,6 +13,13 @@ macro_rules! unimpl {
 }
 
 #[macro_export]
+macro_rules! semantically_unreachable {
+	() => {
+		unsafe { unreachable_unchecked() }
+	};
+}
+
+#[macro_export]
 macro_rules! checked_unwrap_option {
 	($expr:expr) => {
 		$expr.unwrap_or_else(|| unsafe { unreachable_unchecked() })
@@ -38,7 +45,8 @@ macro_rules! checked_match {
 	($expr:expr, $pat:pat, $block:block) => {
 		match $expr {
 			$pat => $block,
-			_ => unsafe { unreachable_unchecked() },
+			// _ => unsafe { unreachable_unchecked() },
+			_ => semantically_unreachable!()
 			}
 	};
 }

### 2020-01-24 src/main.rs

@@ -12,10 +12,7 @@ use cranelift_faerie::{FaerieBackend, FaerieBuilder, FaerieTrapCollection};
 use cranelift_simplejit::{SimpleJITBackend, SimpleJITBuilder};
 use target_lexicon::triple;
 
-use zydis::{
-	AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer,
-	Signedness,
-};
+use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
 
 use structopt::StructOpt;
 
@@ -29,6 +26,9 @@ struct Opt {
 	/// Source code file
 	#[structopt(name = "source", parse(from_os_str))]
 	src: PathBuf,
+
+	#[structopt(name = "output", parse(from_os_str), short = "o")]
+	out: Option<PathBuf>,
 
 	/// Function
 	#[structopt(name = "function", short = "f")]
@@ -52,38 +52,26 @@ fn main() {
 		let mut am = backend::AbstractMachine::<'_, SimpleJITBackend>::new(&tu, builder);
 		if let Some(fname) = &opt.fname {
 			if let Some((fptr, flen)) = am.compiled_function(fname.as_str()) {
-				let fptr = unsafe {
-					slice::from_raw_parts(mem::transmute::<_, *const u8>(fptr), flen as _)
-				};
+				let fptr = unsafe { slice::from_raw_parts(mem::transmute::<_, *const u8>(fptr), flen as _) };
 
 				let asm_formatter = {
-					let mut fm = Formatter::new(FormatterStyle::INTEL)
-						.expect("failed to create assembly formatter");
-					fm.set_property(FormatterProperty::HexUppercase(false))
-						.expect("failed to disable hex uppercase");
-					fm.set_property(FormatterProperty::DisplacementSignedness(Signedness::SIGNED))
-						.expect("failed to set displacement signedness");
-					fm.set_property(FormatterProperty::ImmediateSignedness(Signedness::SIGNED))
-						.expect("failed to set immediate signedness");
-					fm.set_property(FormatterProperty::ForceRelativeRiprel(true))
-						.expect("failed to force relative RIP");
-					fm.set_property(FormatterProperty::AddressSignedness(Signedness::SIGNED))
-						.expect("failed to set address signedness");
-					fm.set_property(FormatterProperty::ForceRelativeBranches(true))
-						.expect("failed to set relative branches");
[…]

### 2020-01-28 paper/tool.tex
fix pointer arithmetic

@@
 	Beside data and control flow, high-level types are also important in program analysis,
-	indeed type reconstruction is an essential step in binary code decompilation.
+	indeed type recovery is an essential step in binary code decompilation.
 	For the purpose of anti-decompilation, the paper introduces a novel obfuscation
@@
 most of information about high-level types is lost in compilation, the binary code
-\emph{type reconstruction} requires special techniques, a survey up until 2015 can be
+\emph{type recovery} requires special techniques, a survey up until 2015 can be
 referenced in~\cite{caballero_type_2016}.
@@
 program analysis, current obfuscation techniques~\cite{collberg_surreptitious_2009} focus mostly
-on hiding them. But to the best of our knowledge, there is still no explicit effort in hiding
+on them. But to the best of our knowledge, there is still no explicit effort in obfuscating
 high-level types. There would be several reasons for this lack of effort.
 
-\emph{First}, type obfuscation can be obtained as side effects of data or control flow obfuscation.
-Indeed, type reconstruction algorithms need both data and control flow to build type constraints,
+\emph{First}, type obfuscation is unsurprisingly a side effect of data or control flow obfuscation.
+Indeed, type recovery algorithms need both data and control flow to build type constraints,
 if any of them is hidden
-then the algorithms cannot work correctly. Or if the function boundary cannot be found
-(because of anti-disassembing tricks, for example), then there are no inputs (i.e. high-level
-objects) for type reconstruction. \emph{Second}, high-level types seem too coarse to be worthy
+then the algorithms cannot work correctly. Or if the function boundary is not found
+(because of anti-disassembing tricks, for example), then high-level objects cannot be recognized.
+\emph{Second}, high-level types seem too coarse to be worthy
 of being protected, in many cases just knowing certain values of the input which make the program
@@
 We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types.
-Our effort is to attack the core of type reconstruction algorithms,
-that is the data flow used to build type constraints, and the \emph{semantic gap} between types in the high-level language and their
-representations in low-level machine code. For that purpose, \emph{uCc} uses extensively
+The compiler is implemented in Rust, its source code and a short user guide are given at (cite).
+Our effort is to attack the core of type recovery algorithms,
+these are the data flow used to build type constraints, and the \emph{semantic gap} between types in the high-level language and their
+representations in the low-level machine code. Beside custom tricks, \emph{uCc} uses extensively
 obfuscation transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
-To increase code diversity, it is a \emph{probabilistic} compiler: given the source
+To make some code diversity, the compiler is \emph{probabilistic}: given a source
 code, \emph{uCc} generates each time a different (but computationally equivalent) output machine code.
 
-The compiler is implemented in Rust, uses \emph{cranelift}~\cite{noauthor_cranelift_nodate} as
-backend. The source code and a short user guide are at (cite). We test outputs of
-\emph{uCc} against decent decompilers, table~\ref{flattening} show experimental results
+We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
+tested functions and their types in source code, table~\ref{flattening} shows results of using
+decompilers to decompile binaries generated by \emph{uCc}. The test suite is also available at
+the repository.
 
@@
 	\begin{center}
-		\caption{Functions and original types}
+		\caption{Functions and original types}\label{description}
 		\begin{tabular}{|l|l|}

### 2020-01-28 demo/sum.c

@@ -1,7 +1,7 @@
-int sum(short *a, int n) {
-	int sum = 0;
+long sum(short *a, int n) {
+	long sum = 0;
 	int i = 0;
-	int *a_i;
+	short *a_i;
 	for (; i < n; i++) {
 		a_i = a + i;
 		sum += *a_i;

### 2020-01-28 src/backend/function.rs

@@ -18,18 +18,11 @@ use cranelift_module::{Backend, FuncId, Module};
 
 use crate::{
 	checked_if_let, checked_match, checked_unwrap_option,
-	frontend::syntax::{
-		BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator,
-		FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
-		WhileStatement,
-	},
+	frontend::syntax::{BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression, WhileStatement},
 	generate_random_maps, semantically_unreachable, unimpl,
 };
 
-use super::support::{
-	evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue, EffectiveType, FunctionIdentifier, FunctionType,
-	NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment,
-};
+use super::support::{evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment};
 
 static NEW_VAR_ID: AtomicUsize = AtomicUsize::new(0);
 
@@ -70,7 +63,7 @@ pub fn get_function_signature(func_def: &'_ FunctionDefinition<'_>, pointer_ty: 
 				match specifier {
[…]

### 2020-01-28 src/main.rs

@@ -14,36 +14,56 @@ use target_lexicon::triple;
 
 use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
 
-use structopt::StructOpt;
+use gumdrop::Options;
+// use structopt::StructOpt;
 
 mod backend;
 mod frontend;
 mod helper;
 
-#[derive(StructOpt)]
-#[structopt(name = "tocc", about = "A type-obfuscated C compiler")]
+// #[derive(StructOpt)]
+// #[structopt(name = "tocc", about = "A type-obfuscated C compiler")]
+// struct Opt {
+// 	/// Source code file
+// 	#[structopt(name = "source", parse(from_os_str))]
+// 	src: PathBuf,
+
+// 	#[structopt(name = "output", parse(from_os_str), short = "o")]
+// 	out: Option<PathBuf>,
+
+// 	/// Function
+// 	#[structopt(name = "function", short = "f")]
+// 	fname: Option<String>,
+
+// 	/// JIT compilation
+// 	#[structopt(name = "code generation mode", short = "j")]
+// 	jit: bool,
+// }
+
+#[derive(Options)]
 struct Opt {
-	/// Source code file
-	#[structopt(name = "source", parse(from_os_str))]
-	src: PathBuf,
+	#[options(help = "print usage")]
+	help: bool,
 
-	#[structopt(name = "output", parse(from_os_str), short = "o")]
-	out: Option<PathBuf>,
+	#[options(free, help = "source code file")]
+	src: String,
 
-	/// Function
-	#[structopt(name = "function", short = "f")]
+	#[options(help = "output object file", meta = "output", no_long)]
+	out: Option<String>,
+
+	#[options(help = "function to jit", meta = "function", no_long)]
 	fname: Option<String>,
 
-	/// JIT compilation
-	#[structopt(name = "code generation mode", short = "j")]
+	#[options(help = "jit", no_long)]
 	jit: bool,
 }
 
 fn main() {
-	let opt = Opt::from_args();
-	let src = opt.src.as_path();
+	// let opt = Opt::from_args();
+	let opt = Opt::parse_args_default_or_exit();
+	// let src = opt.src.as_path();
 
-	let src_code = fs::read_to_string(src).expect("failed to read source code file");
+	let src_code = fs::read_to_string(&opt.src).expect("failed to read source code file");
[…]

### 2020-01-28 paper/tool.tex
shift left/right operators

@@
 %
+\usepackage{amsmath,amssymb}
 \usepackage{graphicx}
@@
 	indeed type recovery is an essential step in binary code decompilation.
-	For the purpose of anti-decompilation, the paper introduces a novel obfuscation
+	For the purpose of anti-decompilation, the paper presents a novel obfuscation
 	technique which makes types become harder to be reconstructed.
@@
 objects~\cite{balakrishnan_divine_2007} (e.g. registers, raw memory accesses, machine
-instructions) before annotate them with types of the supposed original language. Because
-most of information about high-level types is lost in compilation, the binary code
-\emph{type recovery} requires special techniques, a survey up until 2015 can be
-referenced in~\cite{caballero_type_2016}.
+instructions) before annotate them with types of the "assumed" original language.
+In a statically typed language like C, the compiler does not preserve the high-level
+type information in the generated machine code,
+% Because most of information about high-level types is lost in compilation,
+% the machine code
+then the \emph{type recovery} (or type reconstruction) from machine code requires
+special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}.
 
@@
 general code analysis) harder. Since the data and control flow are principal elements for the
-program analysis, current obfuscation techniques~\cite{collberg_surreptitious_2009} focus mostly
+program analysis, current obfuscation methods~\cite{collberg_surreptitious_2009} focus mostly
 on them. But to the best of our knowledge, there is still no explicit effort in obfuscating
@@
 \emph{First}, type obfuscation is unsurprisingly a side effect of data or control flow obfuscation.
-Indeed, type recovery algorithms need both data and control flow to build type constraints,
+Indeed, type reconstruction algorithms need both data and control flow to build type constraints,
 if any of them is hidden
@@
 \section{Type flattening compiler}
-We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types.
-The compiler is implemented in Rust, its source code and a short user guide are given at (cite).
-Our effort is to attack the core of type recovery algorithms,
+We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, its
+objective is to make reconstructing types from machine codes harder.
+It is implemented in Rust, the source code and a brief user guide are given at (cite).
+Our effort is to attack the core of type reconstruction algorithms,
 these are the data flow used to build type constraints, and the \emph{semantic gap} between types in the high-level language and their
-representations in the low-level machine code. Beside custom tricks, \emph{uCc} uses extensively
+representations in the low-level machine code.
+Beside custom tricks, \emph{uCc} uses extensively
 obfuscation transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
@@
 We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
-tested functions and their types in source code, table~\ref{flattening} shows results of using
-decompilers to decompile binaries generated by \emph{uCc}. The test suite is also available at
+tested functions and their types in source codes, table~\ref{flattening} shows results of using
+$4$ decompilers to decompile binaries generated by \emph{uCc}. The test suite is available at
 the repository.
@@
 			\hline
-			modular & \texttt{int mod(int)} \\
+			modular & \texttt{char mod(short, char)} \\
 			\hline
-			increase pointer then dereference & \texttt{int inc\_deref(int*)} \\
+			increase $p$ then dereference & \texttt{int inc\_deref(int *p)} \\
+			\hline
+			strlen  & \texttt{int slen(char*)} \\
+			\hline
+			sum of array $a$ & \texttt{long sum(short *a, int n)} \\
+			\hline
+			$n$-th fibonaci number & \texttt{int fibo(int n)} \\
+			\hline
+			num. of steps until $n \rightsquigarrow 1$ (Collatz's conj.)  & \texttt{int collatz(int n)} \\
 			\hline
@@
 				\hline
+				\texttt{int slen(char*)} & \texttt{int64 slen(int64)} & \texttt{ulong slen(ulong)} &
+				\texttt{ulong slen(undefined8)} & \texttt{int64 slen(uint64)} \\
+				\hline
+				\texttt{long sum(short*, int)} & \texttt{int64 sum(int64, uint64)} & \texttt{ulong sum(ulong, ulong)} & \texttt{undefined8 sum(undefined8)} & sn \\
+				\hline
+				\texttt{int fibo(int)} & \texttt{int64 fibo(uint64)} & \texttt{ulong fibo(ulong)} &
+				\texttt{ulong fibo(undefined8)} & \texttt{int64 fibo(int64)} \\
+				\hline
+				\texttt{int collatz(int)} & \texttt{int64 collatz(int64)} & \texttt{ulong collatz(ulong)} &
+				\texttt{ulong collatz(undefined8)} & \texttt{int64 collatz(int64)} \\
+				\hline
 			\end{tabular}
@@
 \end{table}
+
+It may worth noting that \emph{uCc} makes no effort in making disassembling or function
+boundary detection hard. Indeed, functions in tested binaries are perfectly detectable,
+disassemblable and decompilable.
 

### 2020-01-28 demo/sum.c

@@ -1,10 +1,9 @@
 long sum(short *a, int n) {
 	long sum = 0;
 	int i = 0;
-	short *a_i;
 	for (; i < n; i++) {
-		a_i = a + i;
-		sum += *a_i;
+		a++;
+		sum += *a;
 	}
 	return sum;
 }

### 2020-01-28 src/backend/function.rs

@@ -421,7 +421,7 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 			};
 
 			let pv = checked_unwrap_option!(self.uextend(val_ty, pv));
-			partitioned_values.push(self.logical_shl_imm(pv, offset));
+			partitioned_values.push(self.shl_imm(pv, offset));
 
 			offset += ty.bits() as i32;
 		}
@@ -1054,6 +1054,9 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					BitwiseXor => checked_if_let!(PrimitiveTy(_), &rhs_ty, { ValueTy(self.bxor_imm(rhs_val, lhs_val)) }),
 					BitwiseOr => checked_if_let!(PrimitiveTy(_), &rhs_ty, { ValueTy(self.bor_imm(rhs_val, lhs_val)) }),
 
+					BitwiseLeftShift => ValueTy(self.shl(self.iconst(types::I64, lhs_val), rhs_val)),
+					BitwiseRightShift => ValueTy(self.arithmetic_shr(self.iconst(types::I64, lhs_val), rhs_val)),
+
 					Less => ValueTy(self.icmp_imm(IntCC::SignedGreaterThan, rhs_val, lhs_val)),
 					LessOrEqual => ValueTy(self.icmp_imm(IntCC::SignedGreaterThanOrEqual, rhs_val, lhs_val)),
 					Greater => ValueTy(self.icmp_imm(IntCC::SignedLessThan, rhs_val, lhs_val)),
@@ -1238,6 +1241,8 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					BitwiseAnd => ValueTy(self.band(lhs_val, rhs_val)),
 					BitwiseOr => ValueTy(self.bor(lhs_val, rhs_val)),
 					BitwiseXor => ValueTy(self.bxor(lhs_val, rhs_val)),
+					BitwiseLeftShift => ValueTy(self.shl(lhs_val, rhs_val)),
+					BitwiseRightShift => ValueTy(self.arithmetic_shr(lhs_val, rhs_val)),
 
 					Less => ValueTy(self.icmp(IntCC::SignedLessThan, lhs_val, rhs_val)),
 					LessOrEqual => ValueTy(self.icmp(IntCC::SignedLessThanOrEqual, lhs_val, rhs_val)),
[…]

### 2020-01-28 src/backend/support.rs

@@ -10,10 +10,7 @@ use crate::{
 	checked_if_let, checked_unwrap_option,
 	frontend::{
 		semantics::Environment,
-		syntax::{
-			BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression, Identifier, StructType, TypeSpecifier,
-			UnaryOperator, UnaryOperatorExpression,
-		},
+		syntax::{BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression, Identifier, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression},
 	},
 };
 
@@ -64,12 +61,7 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 		// struct type definition: each declaration is a field declaration
 		let StructType { declarations, .. } = self;
 		let declarations = checked_unwrap_option!(declarations.as_ref());
-		let fields: Vec<(&str, Type)> = declarations
-			.iter()
-			.map(|Declaration { specifier, declarator }| {
-				checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, { (*ident, specifier.into()) })
-			})
-			.collect();
+		let fields: Vec<(&str, Type)> = declarations.iter().map(|Declaration { specifier, declarator }| checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, { (*ident, specifier.into()) })).collect();
 		AggregateType { fields }
 	}
 }

### 2020-01-28 src/backend/translation.rs

@@ -13,9 +13,7 @@ use super::{
 	support::{AggregateType, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment},
 };
 
-pub fn compile<'clif, 'tcx>(
-	tu: &'tcx TranslationUnit, module: &'clif mut Module<impl Backend>, name_env: &'_ mut NameBindingEnvironment<'tcx>, type_env: &'_ mut TypeBindingEnvironment<'tcx>,
-) -> Vec<(FuncId, usize)> {
+pub fn compile<'clif, 'tcx>(tu: &'tcx TranslationUnit, module: &'clif mut Module<impl Backend>, name_env: &'_ mut NameBindingEnvironment<'tcx>, type_env: &'_ mut TypeBindingEnvironment<'tcx>) -> Vec<(FuncId, usize)> {
 	use ExternalDeclaration::*;
 	use TypeSpecifier::*;
 
@@ -36,13 +34,7 @@ pub fn compile<'clif, 'tcx>(
 
 				let func_id = checked_unwrap_result!(module.declare_function(fname, Linkage::Export, &ctxt.func.signature));
 
-				name_env.bind(
-					fname,
-					SimpleTypedIdentifier::FunctionIdent(FunctionIdentifier {
-						ident: func_id,
-						ty: EffectiveType::FunctionTy(FunctionType { return_ty, param_ty: param_ty.clone() }),
-					}),
-				);
+				name_env.bind(fname, SimpleTypedIdentifier::FunctionIdent(FunctionIdentifier { ident: func_id, ty: EffectiveType::FunctionTy(FunctionType { return_ty, param_ty: param_ty.clone() }) }));
 
 				let func = translate_function(func_def, func_id, return_ty, &param_ty, pointer_ty, &mut ctxt, module, name_env, type_env);
 				sfuncs.push(func);

### 2020-01-28 src/frontend/semantics.rs

@@ -2,11 +2,7 @@
 
 use std::{borrow::Borrow, cmp, collections::HashMap, hash::Hash, hint::unreachable_unchecked, i16, i32, i64, i8, marker::PhantomData};
 
-use super::syntax::{
-	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator,
-	FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier, UnaryOperator,
-	UnaryOperatorExpression,
-};
+use super::syntax::{BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression};
 
 use crate::{checked_match, checked_unwrap_option, error, semantically_unreachable, unimpl};
 
@@ -315,7 +311,7 @@ impl<'a> SimpleType<'a> {
 						_ => error!("invalid operation"),
 					},
 
-					BitwiseAnd | BitwiseXor | BitwiseOr => match (lhs_ty, rhs_ty) {
+					BitwiseAnd | BitwiseXor | BitwiseOr | BitwiseLeftShift | BitwiseRightShift => match (lhs_ty, rhs_ty) {
 						(PrimitiveTy(lhs_ty), PrimitiveTy(rhs_ty)) => PrimitiveTy(cmp::max(lhs_ty, rhs_ty)),
 						_ => error!("invalid operation"),
 					},

### 2020-01-28 src/frontend/syntax.rs

@@ -41,6 +41,8 @@ pub enum BinaryOperator {
 	BitwiseAnd,
 	BitwiseXor,
 	BitwiseOr,
+	BitwiseLeftShift,
+	BitwiseRightShift,
 }
 
 #[derive(Clone, Debug)]
@@ -322,6 +324,20 @@ peg::parser! {grammar parser() for str {
 		a:(@) blank()* "|" blank()* b:@ {
 			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
 				operator: BinaryOperator::BitwiseOr,
+				lhs: Box::new(a),
+				rhs: Box::new(b)
+			})
+		}
+		a:(@) blank()* "<<" blank()* b:@ {
+			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
+				operator: BinaryOperator::BitwiseLeftShift,
+				lhs: Box::new(a),
+				rhs: Box::new(b)
+			})
+		}
+		a:(@) blank()* ">>" blank()* b:@ {
+			Expression::BinaryOperatorExpr(BinaryOperatorExpression {
+				operator: BinaryOperator::BitwiseRightShift,
 				lhs: Box::new(a),
 				rhs: Box::new(b)
 			})

### 2020-01-28 src/helper.rs

@@ -46,7 +46,7 @@ macro_rules! checked_match {
 		match $expr {
 			$pat => $block,
 			// _ => unsafe { unreachable_unchecked() },
-			_ => semantically_unreachable!()
+			_ => semantically_unreachable!(),
 			}
 	};
 }

### 2020-01-29 demo/sdbm.c
add sdbm demo

@@ -1,0 +1,8 @@
+int sdbm(char *s) {
+	int hash = 0;
+	while (*s != 0) {
+		hash = *s + (hash << 6) + (hash << 16) - hash;
+		s++;
+	}
+	return hash;
+}

### 2020-01-29 paper/tool.tex
update

@@
 \section{Type flattening compiler}
-We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, its
-objective is to make reconstructing types from machine codes harder.
-It is implemented in Rust, the source code and a brief user guide are given at (cite).
+We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, \emph{uCc}'s
+objective is to make reconstructing C types from machine codes harder.
+The compiler is implemented in Rust, the source code and a brief user guide are given at (cite); different
+from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate} as
+backend.
+
 Our effort is to attack the core of type reconstruction algorithms,
@@
 representations in the low-level machine code.
-Beside custom tricks, \emph{uCc} uses extensively
+Beside custom tricks which would be fully presented in another paper, \emph{uCc} uses extensively
 obfuscation transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
@@
 			\hline
-			increase $p$ then dereference & \texttt{int inc\_deref(int *p)} \\
+			increase $p \leftarrow p + 1$ then dereference & \texttt{int inc\_deref(int *p)} \\
 			\hline
-			strlen  & \texttt{int slen(char*)} \\
+			strlen  & \texttt{int slen(char* s)} \\
 			\hline
@@
 			\hline
-			$n$-th fibonaci number & \texttt{int fibo(int n)} \\
+			$n$-th fibonaci number (recursive impl.) & \texttt{int fibo(int n)} \\
 			\hline
 			num. of steps until $n \rightsquigarrow 1$ (Collatz's conj.)  & \texttt{int collatz(int n)} \\
+			\hline
+			sdbm hash & \texttt{int sdbm(char *s)} \\
 			\hline
@@
 				\texttt{ulong collatz(undefined8)} & \texttt{int64 collatz(int64)} \\
+				\hline
+				\texttt{int sdbm(char*)} & \texttt{int64 sdbm(uint64)} & jeb & \texttt{ulong sdbm(undefined8)} & sn \\
 				\hline

### 2020-01-29 src/backend/function.rs

@@ -1003,6 +1003,8 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					BitwiseAnd => ConstantTy(lhs & rhs),
 					BitwiseXor => ConstantTy(lhs ^ rhs),
 					BitwiseOr => ConstantTy(lhs | rhs),
+					BitwiseLeftShift => ConstantTy(lhs << rhs),
+					BitwiseRightShift => ConstantTy(lhs >> rhs),
 
 					Less => ValueTy(self.bconst(types::B64, lhs < rhs)),
 					LessOrEqual => ValueTy(self.bconst(types::B64, lhs <= rhs)),
@@ -1111,6 +1113,8 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					BitwiseAnd => checked_if_let!(PrimitiveTy(_), &lhs_ty, { ValueTy(self.band_imm(lhs_val, rhs_val)) }),
 					BitwiseXor => checked_if_let!(PrimitiveTy(_), &lhs_ty, { ValueTy(self.bxor_imm(lhs_val, rhs_val)) }),
 					BitwiseOr => checked_if_let!(PrimitiveTy(_), &lhs_ty, { ValueTy(self.bor_imm(lhs_val, rhs_val)) }),
+					BitwiseLeftShift => checked_if_let!(PrimitiveTy(_), &lhs_ty, { ValueTy(self.shl_imm(lhs_val, rhs_val)) }),
+					BitwiseRightShift => checked_if_let!(PrimitiveTy(_), &lhs_ty, { ValueTy(self.arithmetic_shr_imm(lhs_val, rhs_val)) }),
 
 					Less => ValueTy(self.icmp_imm(IntCC::SignedLessThan, lhs_val, rhs_val)),
 					LessOrEqual => ValueTy(self.icmp_imm(IntCC::SignedLessThanOrEqual, lhs_val, rhs_val)),
@@ -1206,7 +1210,7 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 				let lhs_val = self.blur_value(lhs_val);
 				let rhs_val = self.blur_value(rhs_val);
 				let val = match operator {
-					Multiplication => ValueTy(self.iadd(lhs_val, rhs_val)),
+					Multiplication => ValueTy(self.imul(lhs_val, rhs_val)),
[…]

### 2020-01-29 paper/tool.tex
add djb

@@
 
-We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
+We test outputs of \emph{uCc} against some decompilers (the test suite is available at
+the repository). Table~\ref{description} describes briefly
 tested functions and their types in source codes, table~\ref{flattening} shows results of using
-$4$ decompilers to decompile binaries generated by \emph{uCc}. The test suite is available at
-the repository.
+$4$ decompilers to decompile binaries generated by \emph{uCc}.
+No one between tested decompilers can recognize the precise signature of tested functions.
+Basically, any argument is assigned by either \texttt{int64} or \texttt{uint64},
+the highest types in the \emph{conversion rank} of integer types, we call this effect \emph{type flattening}.
+
+We may note that if the tested functions are
+compiled by, \emph{clang} for example, then their signatures can be recognized precisely
+by the decompilers. Last but not least, \emph{uCc} makes no effort in making disassembling or function
+boundary detection hard. Indeed, functions in tested binaries are perfectly detectable,
+disassemblable and decompilable.
 
@@
 			\hline
+			sdbm hash & \texttt{int sdbm(char *s)} \\
+			\hline
+			djb2 hash & \texttt{int djb2(char *s)} \\
+			\hline
 			sum of array $a$ & \texttt{long sum(short *a, int n)} \\
@@
 			num. of steps until $n \rightsquigarrow 1$ (Collatz's conj.)  & \texttt{int collatz(int n)} \\
-			\hline
-			sdbm hash & \texttt{int sdbm(char *s)} \\
 			\hline
@@
 				\hline
-				\texttt{long sum(short*, int)} & \texttt{int64 sum(int64, uint64)} & \texttt{ulong sum(ulong, ulong)} & \texttt{undefined8 sum(undefined8)} & sn \\
+				\texttt{int sdbm(char*)} & \texttt{int64 sdbm(uint64)} & \texttt{ulong sdbm(ulong)} &
+				\texttt{ulong sdbm(undefined8)} & \texttt{int64 sdbm(uint64)} \\
+				\hline
+				\texttt{int djb2(char*)} & \texttt{int64 djb2(uint64)} & \texttt{ulong djb2(ulong)} &
+				\texttt{ulong djb2(undefined8)} & \texttt{int64 djb2(uint64)} \\
+				\hline
+				\texttt{long sum(short*, int)} & \texttt{int64 sum(int64, uint64)} &
+				\texttt{ulong sum(ulong, ulong)} & \texttt{undefined8 sum(undefined8)} & \texttt{int64 sum(uint64, int64)} \\
 				\hline
@@
 				\hline
-				\texttt{int sdbm(char*)} & \texttt{int64 sdbm(uint64)} & jeb & \texttt{ulong sdbm(undefined8)} & sn \\
-				\hline
 			\end{tabular}
@@
 \end{table}
-
-It may worth noting that \emph{uCc} makes no effort in making disassembling or function
-boundary detection hard. Indeed, functions in tested binaries are perfectly detectable,
-disassemblable and decompilable.
 

### 2020-01-29 demo/djb2.c

@@ -1,0 +1,8 @@
+int djb2(char *s) {
+	int hash = 5381;
+	while (*s != 0) {
+		hash = ((hash << 5) + hash) + *s;
+		s++;
+	}
+	return hash;
+}

### 2020-01-30 paper/tool.tex
update

@@
 The compiler is implemented in Rust, the source code and a brief user guide are given at (cite); different
-from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate} as
-backend.
+from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate}
+as backend.
 
@@
 representations in the low-level machine code.
-Beside custom tricks which would be fully presented in another paper, \emph{uCc} uses extensively
+Beside custom tricks, \emph{uCc} uses extensively
 obfuscation transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
@@
 
-We test outputs of \emph{uCc} against some decompilers (the test suite is available at
-the repository). Table~\ref{description} describes briefly
-tested functions and their types in source codes, table~\ref{flattening} shows results of using
-$4$ decompilers to decompile binaries generated by \emph{uCc}.
-No one between tested decompilers can recognize the precise signature of tested functions.
-Basically, any argument is assigned by either \texttt{int64} or \texttt{uint64},
-the highest types in the \emph{conversion rank} of integer types, we call this effect \emph{type flattening}.
+We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
+tested functions and their types in source codes, table~\ref{flattening} shows results of
+decompilers on binaries generated by \emph{uCc}. The effect of obfuscation is to make the types
+of functions harder to be reconstructed. Indeed, the compilers know very little about the original
+types. Basically, any argument in the function signature is simply assigned by either \texttt{int64}
+or \texttt{uint64}, the highest types in the \emph{conversion rank} of integer types, we call this
+effect \emph{type flattening}.
 
-We may note that if the tested functions are
-compiled by, \emph{clang} for example, then their signatures can be recognized precisely
+It may worth to note that the \emph{type flattening} is given by \emph{uCc}, not by the source code
+complexity of tested functions. Indeed if they are compiled by, \emph{clang} or \emph{gcc} for example,
+then their signatures are reconstructed precisely
 by the decompilers. Last but not least, \emph{uCc} makes no effort in making disassembling or function
-boundary detection hard. Indeed, functions in tested binaries are perfectly detectable,
+boundary detection hard: functions in tested binaries are perfectly detectable,
 disassemblable and decompilable.

### 2020-01-30 paper/tool.tex
add option for lightweight obfuscation

@@
 then their signatures are reconstructed precisely
-by the decompilers. Last but not least, \emph{uCc} makes no effort in making disassembling or function
-boundary detection hard: functions in tested binaries are perfectly detectable,
-disassemblable and decompilable.
+by the decompilers. Last but not least, \emph{uCc} attacks directly on type reconstruction algorithms,
+it does not use obfuscation tricks
+% , for example making disassembling or function boundary detection hard,
+which make side effects on type
+reconstruction: functions in tested binaries are perfectly detectable, disassemblable and
+decompilable.
 

### 2020-01-30 src/backend/function.rs

@@ -19,7 +19,7 @@ use cranelift_module::{Backend, FuncId, Module};
 use crate::{
 	checked_if_let, checked_match, checked_unwrap_option,
 	frontend::syntax::{BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression, WhileStatement},
-	generate_random_maps, semantically_unreachable, unimpl,
+	generate_random_maps, light, semantically_unreachable, unimpl,
 };
 
 use super::support::{evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment};
@@ -139,6 +139,10 @@ fn blur_bor(fb: &'_ mut FunctionBuilder, x: Value, y: Value) -> Value {
 }
 
 fn blur_value(fb: &'_ mut FunctionBuilder, val: Value) -> Value {
+	if light() {
+		return val;
+	}
+
 	let val_ty = fb.func.dfg.value_type(val);
 	let val_size = val_ty.bytes();
 
@@ -430,6 +434,10 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 	}
 
 	fn blur_value(&'_ self, val: Value) -> Value {
+		if light() {
+			return val;
+		}
+
 		let val_ty = self.value_type(val);
 		let val_size = val_ty.bytes();
 
@@ -1591,12 +1599,12 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 
 	fn blur_iadd(&'_ self, x: Value, y: Value) -> Value {
 		let (x, y) = self.normalize(x, y);
-		self.iadd(self.bor(x, y), self.band(x, y))
[…]

### 2020-01-30 src/main.rs

@@ -13,9 +13,9 @@ use cranelift_simplejit::{SimpleJITBackend, SimpleJITBuilder};
 use target_lexicon::triple;
 
 use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
-
 use gumdrop::Options;
 // use structopt::StructOpt;
+use once_cell::sync::OnceCell;
 
 mod backend;
 mod frontend;
@@ -51,6 +51,9 @@ struct Opt {
 	#[options(help = "output object file", meta = "output", no_long)]
 	out: Option<String>,
 
+	#[options(help = "lightweight obfuscation", no_long)]
+	light: bool,
+
 	#[options(help = "function to jit", meta = "function", no_long)]
 	fname: Option<String>,
 
@@ -58,10 +61,17 @@ struct Opt {
 	jit: bool,
 }
 
+static LIGHT_BLUR: OnceCell<bool> = OnceCell::new();
+
+pub fn light() -> bool {
+	*LIGHT_BLUR.get_or_init(|| false)
+}
+
 fn main() {
 	// let opt = Opt::from_args();
 	let opt = Opt::parse_args_default_or_exit();
 	// let src = opt.src.as_path();
+	LIGHT_BLUR.set(opt.light).unwrap();
 
 	let src_code = fs::read_to_string(&opt.src).expect("failed to read source code file");
 	let tu = frontend::syntax::parse(src_code.as_str());

### 2020-01-30 src/backend/function.rs
remove comments and add optimization

@@ -3,6 +3,7 @@ use std::{
 	collections::HashMap,
 	hint::unreachable_unchecked,
 	i16, i32, i64, i8,
+	str::FromStr,
 	sync::atomic::{AtomicUsize, Ordering},
 };
 
@@ -15,22 +16,33 @@ use cranelift_codegen::{
 	Context,
 };
 use cranelift_module::{Backend, FuncId, Module};
+use cranelift_preopt::optimize;
+
+use target_lexicon::triple;
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap_option,
-	frontend::syntax::{BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator, DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression, WhileStatement},
+	checked_if_let, checked_match, checked_unwrap_option, checked_unwrap_result,
+	frontend::syntax::{
+		BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator,
+		DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator,
+		FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement,
+		StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression, WhileStatement,
+	},
 	generate_random_maps, light, semantically_unreachable, unimpl,
 };
 
-use super::support::{evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier, AggregateType, ConcreteValue, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, PointerIdentifer, PrimitiveIdentifier, SimpleTypedConcreteValue, SimpleTypedIdentifier, TypeBindingEnvironment};
+use super::support::{
+	evaluate_constant_arithmetic_expression, generate_random_partition, AggregateIdentifier,
+	AggregateType, ConcreteValue, EffectiveType, FunctionIdentifier, FunctionType,
[…]

### 2020-01-30 src/frontend/semantics.rs

@@ -362,7 +362,6 @@ impl<'a> SimpleType<'a> {
 						})
 						.collect();
 
-					// let sname = sname.into();
 					env.bind(identifier.into(), Self::AggregateTy(AggregateType { fields }));
 				}
 
@@ -522,10 +521,6 @@ pub fn check_statement<'a>(stmt: &'_ Statement<'a>, bind_env: &'_ mut BindingEnv
 						(PointerTy(_), PrimitiveTy(_)) => {}
 						_ => todo!(),
 					}
-
-					// if *return_ty != expr_ty {
-					// 	error!("returned expression ill-typed")
-					// }
 				}
 			}
 		}

### 2020-01-30 src/frontend/syntax.rs

@@ -659,28 +659,4 @@ peg::parser! {grammar parser() for str {
 		}
 }}
 
-// pub fn parse(src_file: impl AsRef<Path>) -> TranslationUnit {
-pub fn parse(src_code: &str) -> TranslationUnit {
-	// let src_code = fs::read_to_string(src_file).expect("Failed to read source code file");
-	if let Ok(tu) = parser::translation_unit(&src_code) { tu } else { panic!("failed to parse source code") }
-}
-
-// pub fn function_name(tu: &TranslationUnit) -> &str {
-// 	let TranslationUnit(extern_decs) = tu;
-
-// 	for dec in extern_decs.iter() {
-// 		use ExternalDeclaration::*;
-// 		if let FunctionDefinitionDecl(FunctionDefinition {
-// 			declarator: FunctionDeclarator {
-// 				identifier: Identifier(fname),
-// 				..
-// 			},
-// 			..
-// 		}) = dec
-// 		{
-// 			return fname.as_str();
-// 		}
-// 	}
-
-// 	panic!("No function in the translation unit")
-// }
+pub fn parse(src_code: &str) -> TranslationUnit { if let Ok(tu) = parser::translation_unit(&src_code) { tu } else { panic!("failed to parse source code") } }

### 2020-01-30 src/helper.rs

@@ -45,7 +45,6 @@ macro_rules! checked_match {
 	($expr:expr, $pat:pat, $block:block) => {
 		match $expr {
 			$pat => $block,
-			// _ => unsafe { unreachable_unchecked() },
 			_ => semantically_unreachable!(),
 			}
 	};

### 2020-01-30 src/main.rs

@@ -12,33 +12,13 @@ use cranelift_faerie::{FaerieBackend, FaerieBuilder, FaerieTrapCollection};
 use cranelift_simplejit::{SimpleJITBackend, SimpleJITBuilder};
 use target_lexicon::triple;
 
-use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
 use gumdrop::Options;
-// use structopt::StructOpt;
 use once_cell::sync::OnceCell;
+use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
 
 mod backend;
 mod frontend;
 mod helper;
-
-// #[derive(StructOpt)]
-// #[structopt(name = "tocc", about = "A type-obfuscated C compiler")]
-// struct Opt {
-// 	/// Source code file
-// 	#[structopt(name = "source", parse(from_os_str))]
-// 	src: PathBuf,
-
-// 	#[structopt(name = "output", parse(from_os_str), short = "o")]
-// 	out: Option<PathBuf>,
-
-// 	/// Function
-// 	#[structopt(name = "function", short = "f")]
-// 	fname: Option<String>,
-
-// 	/// JIT compilation
-// 	#[structopt(name = "code generation mode", short = "j")]
-// 	jit: bool,
-// }
 
 #[derive(Options)]
 struct Opt {
@@ -63,14 +43,10 @@ struct Opt {
 
 static LIGHT_BLUR: OnceCell<bool> = OnceCell::new();
 
-pub fn light() -> bool {
-	*LIGHT_BLUR.get_or_init(|| false)
-}
+pub fn light() -> bool { *LIGHT_BLUR.get_or_init(|| false) }
 
 fn main() {
-	// let opt = Opt::from_args();
 	let opt = Opt::parse_args_default_or_exit();
-	// let src = opt.src.as_path();
 	LIGHT_BLUR.set(opt.light).unwrap();
 
 	let src_code = fs::read_to_string(&opt.src).expect("failed to read source code file");
@@ -111,7 +87,6 @@ fn main() {
 	} else {
 		let output = {
 			if let Some(out) = opt.out {
-				// checked_unwrap_option!(out.to_str()).to_owned()
 				out
 			} else {
 				let mut src = PathBuf::from(opt.src);
@@ -154,7 +129,6 @@ mod tests {
 
[…]

### 2020-01-30 paper/tool.tex
update

@@
 % the machine code
-then the \emph{type recovery} (or type reconstruction) from machine code requires
+then the \emph{type reconstruction} (or type recovery) from machine code requires
 special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}.
@@
 \emph{First}, type obfuscation is unsurprisingly a side effect of data or control flow obfuscation.
-Indeed, type reconstruction algorithms need both data and control flow to build type constraints,
+Indeed, type reconstruction algorithms need data and control flow to build type constraints,
 if any of them is hidden
@@
 objective is to make reconstructing C types from machine codes harder.
-The compiler is implemented in Rust, the source code and a brief user guide are given at (cite); different
-from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate}
+The compiler is implemented in Rust, the source code and a brief user guide are given at~\cite{ta_ucc_nodate};
+different from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate}
 as backend.

### 2020-01-30 src/backend.rs

@@ -9,18 +9,19 @@ mod support;
 mod translation;
 
 use crate::frontend::syntax::TranslationUnit;
-use support::{FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment};
+use support::{
+	FunctionIdentifier, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment,
+};
 
 // an abstract machine that runs Cranelift IR
 pub struct AbstractMachine<'s, B: Backend> {
 	module: Module<B>,
 	name_env: NameBindingEnvironment<'s>,
-	compiled_funcs: Vec<(FuncId, usize)>,
+	compiled_funcs: Vec<(FuncId, u32)>,
 }
 
 impl<'s, B: Backend> AbstractMachine<'s, B> {
 	pub fn new(tu: &'s TranslationUnit, builder: B::Builder) -> Self {
-		// let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
 		let mut module = Module::new(builder);
 		let mut name_env = NameBindingEnvironment::new();
 		let mut type_env = TypeBindingEnvironment::new();
@@ -29,11 +30,10 @@ impl<'s, B: Backend> AbstractMachine<'s, B> {
 		AbstractMachine { module, name_env, compiled_funcs }
 	}
 
-	pub fn compiled_function(&mut self, fname: &'_ str) -> Option<(B::FinalizedFunction, usize)> {
+	pub fn compiled_function(&mut self, fname: &'_ str) -> Option<(B::FinalizedFunction, u32)> {
 		let ident = self.name_env.get(fname);
 		if let SimpleTypedIdentifier::FunctionIdent(FunctionIdentifier { ident, .. }) = ident {
 			let (fid, flen) = self.compiled_funcs.iter().find(|(fid, _)| fid == ident)?;
-			// let fptr = translation::jitted_function(*fid, *flen, &mut self.module);
 			let fptr = self.module.get_finalized_function(*fid);
 			Some((fptr, *flen))
 		} else {

### 2020-01-30 src/backend/function.rs

@@ -28,7 +28,7 @@ use crate::{
 		FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement,
 		StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression, WhileStatement,
 	},
-	generate_random_maps, light, semantically_unreachable, unimpl,
+	generate_random_maps, light, semantically_unreachable, unimpl, verbose,
 };
 
 use super::support::{
@@ -286,11 +286,11 @@ fn optimize_function(ctxt: &'_ mut Context) {
 }
 
 pub fn translate_function<'clif, 'tcx>(
-	func_def: &'tcx FunctionDefinition<'tcx>, func_id: FuncId, return_ty: Option<Type>,
-	param_ty: &'_ [Type], pointer_ty: Type, ctxt: &'clif mut Context,
-	module: &'clif mut Module<impl Backend>, outer_name_env: &'_ NameBindingEnvironment<'tcx>,
+	func_def: &'tcx FunctionDefinition<'tcx>, return_ty: Option<Type>, param_ty: &'_ [Type],
+	pointer_ty: Type, ctxt: &'clif mut Context, module: &'clif mut Module<impl Backend>,
+	outer_name_env: &'_ NameBindingEnvironment<'tcx>,
 	outer_type_env: &'_ TypeBindingEnvironment<'tcx>,
-) -> (FuncId, usize) {
+) {
 	let FunctionDefinition { body, .. } = func_def;
 
 	let mut func_builder_ctxt = FunctionBuilderContext::new();
@@ -312,20 +312,18 @@ pub fn translate_function<'clif, 'tcx>(
 		FunctionTranslator::new(func_builder, module, return_ty, name_env, outer_type_env);
 	func_translator.translate_statement(body, entry_ebb);
 	func_translator.func_builder.get_mut().finalize();
-	// println!("{:?}", func_translator.func_builder.borrow().func);
-
-	let func_len = module.define_function(func_id, ctxt).expect("failed to define function");
-
-	module.clear_context(ctxt);
-
-	(func_id, func_len as usize)
 }
 
 pub fn finalize_function_translation<'clif>(
-	module: &'clif mut Module<impl Backend>, ctxt: &'clif mut Context, func_id: FuncId,
-) {
+	func_id: FuncId, ctxt: &'clif mut Context, module: &'clif mut Module<impl Backend>,
+) -> u32 {
 	optimize_function(ctxt);
[…]

### 2020-01-30 src/backend/support.rs

@@ -10,7 +10,11 @@ use crate::{
 	checked_if_let, checked_unwrap_option,
 	frontend::{
 		semantics::Environment,
-		syntax::{BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator, Expression, Identifier, StructType, TypeSpecifier, UnaryOperator, UnaryOperatorExpression},
+		syntax::{
+			BinaryOperator, BinaryOperatorExpression, Constant, Declaration, Declarator,
+			Expression, Identifier, StructType, TypeSpecifier, UnaryOperator,
+			UnaryOperatorExpression,
+		},
 	},
 };
 
@@ -53,7 +57,9 @@ impl AggregateType<'_> {
 		Some(*fty)
 	}
 
-	pub fn bytes(&self) -> usize { self.fields.iter().fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize) }
+	pub fn bytes(&self) -> usize {
+		self.fields.iter().fold(0usize, |sum, (_, fty)| sum + fty.bytes() as usize)
+	}
 }
 
 impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
@@ -61,7 +67,14 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 		// struct type definition: each declaration is a field declaration
 		let StructType { declarations, .. } = self;
 		let declarations = checked_unwrap_option!(declarations.as_ref());
-		let fields: Vec<(&str, Type)> = declarations.iter().map(|Declaration { specifier, declarator }| checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, { (*ident, specifier.into()) })).collect();
+		let fields: Vec<(&str, Type)> = declarations
+			.iter()
+			.map(|Declaration { specifier, declarator }| {
+				checked_if_let!(Some(Declarator { ident: Identifier(ident), .. }), declarator, {
+					(*ident, specifier.into())
+				})
+			})
+			.collect();
 		AggregateType { fields }
 	}
 }
@@ -127,7 +140,6 @@ impl Into<Type> for &TypeSpecifier<'_> {
 }
 
 // binding context
-// pub type NameBindingEnvironment<'a> = HashMap<&'a str, SimpleTypedIdentifier<'a>>;
 pub type NameBindingEnvironment<'a> = Environment<'a, &'a str, SimpleTypedIdentifier<'a>>;
 
 // visible types

### 2020-01-30 src/backend/translation.rs

@@ -4,16 +4,28 @@ use cranelift_module::{Backend, FuncId, Linkage, Module};
 
 use crate::{
 	checked_match, checked_unwrap_result,
-	frontend::syntax::{Declaration, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier, StructType, TranslationUnit, TypeSpecifier},
+	frontend::syntax::{
+		Declaration, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier,
+		StructType, TranslationUnit, TypeSpecifier,
+	},
 	semantically_unreachable,
 };
 
 use super::{
-	function::{blur_function_signature, get_function_signature, translate_function},
-	support::{AggregateType, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment, SimpleTypedIdentifier, TypeBindingEnvironment},
+	function::{
+		blur_function_signature, finalize_function_translation, get_function_signature,
+		translate_function,
+	},
+	support::{
+		AggregateType, EffectiveType, FunctionIdentifier, FunctionType, NameBindingEnvironment,
+		SimpleTypedIdentifier, TypeBindingEnvironment,
+	},
 };
 
-pub fn compile<'clif, 'tcx>(tu: &'tcx TranslationUnit, module: &'clif mut Module<impl Backend>, name_env: &'_ mut NameBindingEnvironment<'tcx>, type_env: &'_ mut TypeBindingEnvironment<'tcx>) -> Vec<(FuncId, usize)> {
+pub fn compile<'clif, 'tcx>(
+	tu: &'tcx TranslationUnit, module: &'clif mut Module<impl Backend>,
+	name_env: &'_ mut NameBindingEnvironment<'tcx>, type_env: &'_ mut TypeBindingEnvironment<'tcx>,
+) -> Vec<(FuncId, u32)> {
 	use ExternalDeclaration::*;
 	use TypeSpecifier::*;
 
@@ -27,17 +39,37 @@ pub fn compile<'clif, 'tcx>(tu: &'tcx TranslationUnit, module: &'clif mut Module
 	for dec in extern_decs {
 		match dec {
 			FunctionDefinitionDecl(func_def) => {
-				let FunctionDefinition { declarator: FunctionDeclarator { identifier: Identifier(fname), .. }, .. } = func_def;
+				let FunctionDefinition {
+					declarator: FunctionDeclarator { identifier: Identifier(fname), .. },
+					..
+				} = func_def;
 
[…]

### 2020-01-30 src/frontend/semantics.rs

@@ -1,8 +1,16 @@
 // semantics analysis
 
-use std::{borrow::Borrow, cmp, collections::HashMap, hash::Hash, hint::unreachable_unchecked, i16, i32, i64, i8, marker::PhantomData};
+use std::{
+	borrow::Borrow, cmp, collections::HashMap, hash::Hash, hint::unreachable_unchecked, i16, i32,
+	i64, i8, marker::PhantomData,
+};
 
-use super::syntax::{BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator, DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType, TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression};
+use super::syntax::{
+	BinaryOperator, BinaryOperatorExpression, CallExpression, Constant, Declaration, Declarator,
+	DerivedDeclarator, Expression, ExternalDeclaration, FunctionDeclarator, FunctionDefinition,
+	Identifier, IfStatement, MemberExpression, MemberOperator, Statement, StructType,
+	TranslationUnit, TypeSpecifier, UnaryOperator, UnaryOperatorExpression,
+};
 
 use crate::{checked_match, checked_unwrap_option, error, semantically_unreachable, unimpl};
 
@@ -96,9 +104,19 @@ where
 		}
 	}
 
-	pub fn get(&self, name: K) -> &T { self.env.get(&name).map(|BoundedType { ty, .. }| ty).unwrap_or_else(|| error!("name not found in current scope")) }
+	pub fn get(&self, name: K) -> &T {
+		self.env
+			.get(&name)
+			.map(|BoundedType { ty, .. }| ty)
+			.unwrap_or_else(|| error!("name not found in current scope"))
+	}
 
-	pub fn get_unchecked(&'_ self, name: K) -> &T { self.env.get(&name).map(|BoundedType { ty, .. }| ty).unwrap_or_else(|| unsafe { unreachable_unchecked() }) }
+	pub fn get_unchecked(&'_ self, name: K) -> &T {
+		self.env
+			.get(&name)
+			.map(|BoundedType { ty, .. }| ty)
+			.unwrap_or_else(|| unsafe { unreachable_unchecked() })
+	}
 }
 
 // map from indentifier to its type
[…]

### 2020-01-30 src/frontend/syntax.rs

@@ -3,7 +3,9 @@ use std::hint::unreachable_unchecked;
 
 use crate::error;
 
-const KEYWORDS: &'_ [&'_ str] = &["if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void"];
+const KEYWORDS: &'_ [&'_ str] = &[
+	"if", "else", "for", "while", "do", "char", "short", "int", "long", "return", "struct", "void",
+];
 
 #[derive(Clone, Debug)]
 pub enum UnaryOperator {
@@ -659,4 +661,10 @@ peg::parser! {grammar parser() for str {
 		}
 }}
 
-pub fn parse(src_code: &str) -> TranslationUnit { if let Ok(tu) = parser::translation_unit(&src_code) { tu } else { panic!("failed to parse source code") } }
+pub fn parse(src_code: &str) -> TranslationUnit {
+	if let Ok(tu) = parser::translation_unit(&src_code) {
+		tu
+	} else {
+		panic!("failed to parse source code")
+	}
+}

### 2020-01-30 src/main.rs

@@ -14,7 +14,10 @@ use target_lexicon::triple;
 
 use gumdrop::Options;
 use once_cell::sync::OnceCell;
-use zydis::{AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer, Signedness};
+use zydis::{
+	AddressWidth, Decoder, Formatter, FormatterProperty, FormatterStyle, MachineMode, OutputBuffer,
+	Signedness,
+};
 
 mod backend;
 mod frontend;
@@ -34,6 +37,9 @@ struct Opt {
 	#[options(help = "lightweight obfuscation", no_long)]
 	light: bool,
 
+	#[options(help = "verbose", no_long)]
+	verbose: bool,
+
 	#[options(help = "function to jit", meta = "function", no_long)]
 	fname: Option<String>,
 
@@ -42,12 +48,15 @@ struct Opt {
 }
 
 static LIGHT_BLUR: OnceCell<bool> = OnceCell::new();
-
 pub fn light() -> bool { *LIGHT_BLUR.get_or_init(|| false) }
+
+static VERBOSE: OnceCell<bool> = OnceCell::new();
+pub fn verbose() -> bool { *VERBOSE.get_or_init(|| false) }
 
 fn main() {
 	let opt = Opt::parse_args_default_or_exit();
 	LIGHT_BLUR.set(opt.light).unwrap();
+	VERBOSE.set(opt.verbose).unwrap();
 
 	let src_code = fs::read_to_string(&opt.src).expect("failed to read source code file");
 	let tu = frontend::syntax::parse(src_code.as_str());
@@ -58,26 +67,38 @@ fn main() {
 		let mut am = backend::AbstractMachine::<'_, SimpleJITBackend>::new(&tu, builder);
 		if let Some(fname) = &opt.fname {
 			if let Some((fptr, flen)) = am.compiled_function(fname.as_str()) {
-				let fptr = unsafe { slice::from_raw_parts(mem::transmute::<_, *const u8>(fptr), flen as _) };
+				let fptr = unsafe {
+					slice::from_raw_parts(mem::transmute::<_, *const u8>(fptr), flen as _)
+				};
 
 				let asm_formatter = {
-					let mut fm = Formatter::new(FormatterStyle::INTEL).expect("failed to create assembly formatter");
-					fm.set_property(FormatterProperty::HexUppercase(false)).expect("failed to disable hex uppercase");
[…]

### 2020-01-31 paper/tool.tex
update

@@
 then the \emph{type reconstruction} (or type recovery) from machine code requires
-special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}.
+special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}, more
+recent research includes~\cite{noonan_polymorphic_2016, maier_typeminer_2019, katz_estimating_2016}.
 
@@
 then the algorithms cannot work correctly. Or if the function boundary is not found
-(because of anti-disassembing tricks, for example), then high-level objects cannot be recognized.
+(because of anti-disassembly tricks, for example), then high-level objects cannot be recognized.
 \emph{Second}, high-level types seem too coarse to be worthy
@@
 
-\section{Type flattening compiler}
+\subsection*{Type flattening obfuscation}
+Under our interest, the studies in binary code type reconstruction can be roughly divided into
+two directions: one is based on semantics of programs, the other is not. We focus on the former,
+and also on methods using static analysis. The research in this vein starts with
+Mycroft~\cite{mycroft_type-based_1999}, and improved in~\cite{lee_tie_2011,noonan_polymorphic_2016,elwazeer_scalable_2013}
+
+\section{Compiler for type flattening}
 We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, \emph{uCc}'s
@@
 
+\subsection*{Evaluation}
 We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
@@
 decompilers on binaries generated by \emph{uCc}. The effect of obfuscation is to make the types
-of functions harder to be reconstructed. Indeed, the compilers know very little about the original
+of functions harder to be reconstructed. Indeed, the decompilers know very little about the original
 types. Basically, any argument in the function signature is simply assigned by either \texttt{int64}
@@
 effect \emph{type flattening}.
-
-It may worth to note that the \emph{type flattening} is given by \emph{uCc}, not by the source code
-complexity of tested functions. Indeed if they are compiled by, \emph{clang} or \emph{gcc} for example,
-then their signatures are reconstructed precisely
-by the decompilers. Last but not least, \emph{uCc} attacks directly on type reconstruction algorithms,
-it does not use obfuscation tricks
-% , for example making disassembling or function boundary detection hard,
-which make side effects on type
-reconstruction: functions in tested binaries are perfectly detectable, disassemblable and
-decompilable.
 
@@
 \end{table}
+
+It may worth to note that the \emph{type flattening} is given by \emph{uCc}, not by the source code
+complexity of tested functions. Indeed if they are compiled by, \emph{clang} or \emph{gcc} for example,
+then their signatures are reconstructed precisely
+by the decompilers. Last but not least, \emph{uCc} attacks directly on type reconstruction algorithms,
+it doesn't use obfuscation techniques
+% , for example making disassembling or function boundary detection hard,
+whose side effects affect the type
+reconstruction. Indeed, functions in tested binaries are perfectly detectable, disassemblable and
+decompilable; only their decompiled types are in question.
 

### 2020-02-02 paper/tool.tex
update

@@
 
-\usepackage{listings}
-\lstset{basicstyle=\small\ttfamily,showspaces=false,frame=tb}
-\lstloadlanguages{C,C++,[x86masm]Assembler}
+% \usepackage{listings}
+% \lstset{basicstyle=\small\ttfamily,showspaces=false,frame=tb}
+% \lstloadlanguages{C,C++,[x86masm]Assembler}
 
@@
 instructions) before annotate them with types of the "assumed" original language.
-In a statically typed language like C, the compiler does not preserve the high-level
+In a statically typed language like C, the compiler doesn't preserve the high-level
 type information in the generated machine code,
@@
 special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}, more
-recent research includes~\cite{noonan_polymorphic_2016, maier_typeminer_2019, katz_estimating_2016}.
+recent research
+includes~\cite{noonan_polymorphic_2016, maier_typeminer_2019, katz_estimating_2016, robbins_minx_2016}.
 
@@
 two directions: one is based on semantics of programs, the other is not. We focus on the former,
-and also on methods using static analysis. The research in this vein starts with
-Mycroft~\cite{mycroft_type-based_1999}, and improved in~\cite{lee_tie_2011,noonan_polymorphic_2016,elwazeer_scalable_2013}
+and also on methods based on static analysis. The research in this vein starts with
+Mycroft~\cite{mycroft_type-based_1999}, and improved
+in~\cite{lee_tie_2011,noonan_polymorphic_2016,elwazeer_scalable_2013, robbins_minx_2016}.
+One of the notable improvement is to propose some notion of \emph{subtyping} to formally estimate
+the closeness of inferred types over the original types. For example, the subtyping
+in~\cite{lee_tie_2011} is based on a lattice which simulates the
+\emph{conversion rank} of C's integer types, e.g. \texttt{int16\_t} is subtype of \texttt{int64\_t}.
+Basically, if the inferred type is a supertype of the original one
+then the result, though may be still sound, is less accurate. We should note that sometimes,
+the supertype is the best result possible.
+
+In this work, we limit on primitive types and their derived pointer types. Our purpose
+is to neutralize the subtyping relation: a type can only be inferred as its
+supertype. Concretely, \texttt{char}, \texttt{short}, \texttt{int}, etc. and pointers will
+be recognized as either \texttt{uint64\_t} or \texttt{int64\_t}. We call this technique
+\emph{type flattening obfuscation}.
+Also we focus only on obfuscating types of function signatures, local variables are weaker primitives
+since the compiler can remove them, e.g. through optimization.
 
 \section{Compiler for type flattening}
-We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, \emph{uCc}'s
-objective is to make reconstructing C types from machine codes harder.
+We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types.
+% \emph{uCc}'s objective is to make reconstructing C types from machine codes harder.
 The compiler is implemented in Rust, the source code and a brief user guide are given at~\cite{ta_ucc_nodate};
-different from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate}
+different from other code obfuscation implementations, it uses cranelift~\cite{noauthor_cranelift_nodate}
 as backend.
 
-Our effort is to attack the core of type reconstruction algorithms,
-these are the data flow used to build type constraints, and the \emph{semantic gap} between types in the high-level language and their
+% Our effort is to
+\emph{uCc} attacks the core of type reconstruction algorithms,
+these are the data flow used to build type constraints and the \emph{semantic gap} between types in the high-level language and their
 representations in the low-level machine code.
 Beside custom tricks, \emph{uCc} uses extensively
-obfuscation transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
+transformations based on Mixed Boolean Arithmetic expressions~\cite{eyrolles_obfuscation_2017,zhou_information_2007}.
 To make some code diversity, the compiler is \emph{probabilistic}: given a source
 code, \emph{uCc} generates each time a different (but computationally equivalent) output machine code.
-
-\subsection*{Evaluation}
-We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
-tested functions and their types in source codes, table~\ref{flattening} shows results of
-decompilers on binaries generated by \emph{uCc}. The effect of obfuscation is to make the types
-of functions harder to be reconstructed. Indeed, the decompilers know very little about the original
-types. Basically, any argument in the function signature is simply assigned by either \texttt{int64}
-or \texttt{uint64}, the highest types in the \emph{conversion rank} of integer types, we call this
-effect \emph{type flattening}.
 
@@
 			\hline
-			Description & Function type \\
+			Description & Signature \\
 			\hline
@@
 \end{table}
+
+\subsection*{Evaluation}
+We test outputs of \emph{uCc} against some decompilers, table~\ref{description} describes briefly
+tested functions and their signatures in source codes, table~\ref{flattening} shows results of
+decompilers on binaries generated by \emph{uCc}.
+% The effect of obfuscation is to make the types of functions harder to be reconstructed.
+% Indeed, the decompilers know very little about the original
+% types:
+Basically, any argument in the function signature is simply assigned by either \texttt{int64}
+or \texttt{uint64}.
+% , the highest types in the \emph{conversion rank} of integer types, we call this
+% effect \emph{type flattening}.
 
@@
 complexity of tested functions. Indeed if they are compiled by, \emph{clang} or \emph{gcc} for example,
-then their signatures are reconstructed precisely
-by the decompilers. Last but not least, \emph{uCc} attacks directly on type reconstruction algorithms,
-it doesn't use obfuscation techniques
+then their signatures can be reconstructed precisely
+by any tested decompiler. Last but not least, \emph{uCc}
+% attacks directly on type reconstruction algorithms,
+% it
+doesn't use obfuscation techniques
 % , for example making disassembling or function boundary detection hard,
-whose side effects affect the type
-reconstruction. Indeed, functions in tested binaries are perfectly detectable, disassemblable and
-decompilable; only their decompiled types are in question.
+whose side effects may affect the type
+reconstruction: functions in tested binaries are perfectly detectable, disassemblable and
+decompilable; only their inferred signatures are in question.
 

### 2020-02-23 src/backend/function.rs
update

@@ -449,13 +449,9 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 			} else {
 				match ty {
 					types::I8 => id!(i8, pv, ty, olevel),
-
 					types::I16 => id!(i16, pv, ty, olevel),
-
 					types::I32 => id!(i32, pv, ty, olevel),
-
 					types::I64 => id!(i64, pv, ty, olevel),
-
 					_ => pv,
 				}
 			};

### 2020-03-01 src/backend/function.rs
update

@@ -89,15 +89,27 @@ pub fn get_function_signature(
 	(return_ty, param_ty)
 }
 
+fn masquerade_function_signature(
+	return_ty: Option<Type>, param_ty: &'_ [Type], topty: Type,
+) -> Signature {
+	Signature {
+		params: param_ty.iter().map(|_| AbiParam::new(topty)).collect(),
+		returns: if return_ty.is_some() { vec![AbiParam::new(topty)] } else { vec![] },
+		call_conv: isa::CallConv::SystemV,
+	}
+}
+
 pub fn blur_function_signature(
 	return_ty: Option<Type>, param_ty: &'_ [Type], pointer_ty: Type, ctxt: &'_ mut Context,
 ) {
-	if return_ty.is_some() {
-		ctxt.func.signature.returns.push(AbiParam::new(pointer_ty));
-	}
-	for _ in param_ty {
-		ctxt.func.signature.params.push(AbiParam::new(pointer_ty));
-	}
+	let sig = masquerade_function_signature(return_ty, param_ty, pointer_ty);
+	ctxt.func.signature = sig;
+	// if return_ty.is_some() {
+	// 	ctxt.func.signature.returns.push(AbiParam::new(pointer_ty));
+	// }
+	// for _ in param_ty {
+	// 	ctxt.func.signature.params.push(AbiParam::new(pointer_ty));
+	// }
 }
 
 fn blur_bor(fb: &'_ mut FunctionBuilder, x: Value, y: Value) -> Value {
@@ -551,6 +563,7 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 		self.blur_value(val)
 	}
 
+	// requirement: no obfuscation applied
 	fn translate_declaration(
 		&'_ mut self, Declaration { specifier, declarator }: &'_ Declaration<'tcx>,
 	) {
@@ -663,6 +676,7 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 		}
 	}
 
+	// requirement: no obfuscation applied
 	fn translate_do_while_statement(
 		&'_ mut self, DoWhileStatement { statement, condition }: &'_ DoWhileStatement<'tcx>,
 		_current_block: Block,
@@ -692,6 +706,7 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 		Some(exit_block)
 	}
 
[…]

### 2020-03-01 src/main.rs

@@ -34,11 +34,11 @@ struct Opt {
 	#[options(help = "output object file", meta = "output", no_long)]
 	out: Option<String>,
 
-	#[options(help = "lightweight obfuscation", no_long)]
+	#[options(help = "only type flattening, nothing more", no_long)]
 	light: bool,
 
 	#[options(
-		help = "heavyweight obfuscation",
+		help = "type flattening, call aliasing, etc.",
 		meta = "level",
 		short = "w",
 		no_long,

### 2020-03-01 src/backend/function.rs
update

@@ -413,9 +413,9 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 			($ty:ty, $pv:expr, $tyv:expr, $olevel:expr) => {
 				if $olevel == 0 {
 					let (a0, b0, a1, b1) = generate_linear_maps!($ty);
-					self.blur_iadd_imm(
-						self.blur_imul_imm(
-							self.blur_iadd_imm(self.blur_imul_imm($pv, a0), b0),
+					self.iadd_imm(
+						self.imul_imm(
+							self.iadd_imm(self.imul_imm($pv, a0), b0),
 							a1,
 						),
 						b1,
@@ -427,10 +427,10 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					for i in 1..=$olevel {
 						let mut xi = x;
 						for _ in 1..i {
-							xi = self.blur_imul(xi, x);
+							xi = self.imul(xi, x);
 						}
-						let ai_xi = self.blur_imul_imm(xi, coeffs[i as usize] as i64);
-						px = self.blur_iadd(px, ai_xi);
+						let ai_xi = self.imul_imm(xi, coeffs[i as usize] as i64);
+						px = self.iadd(px, ai_xi);
 					}
 
 					let x = px;
@@ -438,10 +438,10 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					for i in 1..=$olevel {
 						let mut xi = x;
 						for _ in 1..i {
-							xi = self.blur_imul(xi, x);
+							xi = self.imul(xi, x);
 						}
-						let bi_xi = self.blur_imul_imm(xi, inv_coeffs[i as usize] as i64);
-						qx = self.blur_iadd(qx, bi_xi);
+						let bi_xi = self.imul_imm(xi, inv_coeffs[i as usize] as i64);
+						qx = self.iadd(qx, bi_xi);
 					}
 
 					qx
@@ -487,9 +487,9 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 			($ty:ty, $pv:expr, $tyv:expr, $olevel:expr) => {
 				if $olevel == 0 {
 					let (a0, b0, a1, b1) = generate_linear_maps!($ty);
-					self.blur_iadd_imm(
-						self.blur_imul_imm(
[…]

### 2020-03-01 src/backend/function.rs
update

@@ -139,15 +139,17 @@ fn blur_value(fb: &'_ mut FunctionBuilder, val: Value) -> Value {
 	#[rustfmt::skip]
 	macro_rules! id {
 		($ty:ty, $pv:expr, $tyv:expr, $olevel:expr) => {
-			if $olevel == 0 {
-				let (a0, b0, a1, b1) = generate_linear_maps!($ty);
-				let pv = ins!().imul_imm($pv, a0 as i64);
-				let pv = ins!().iadd_imm(pv, b0 as i64);
-				let pv = ins!().imul_imm(pv, a1 as i64);
-				let pv = ins!().iadd_imm(pv, b1 as i64);
-				pv
-			} else {
+			// if $olevel == 0 {
+			// 	let (a0, b0, a1, b1) = generate_linear_maps!($ty);
+			// 	let pv = ins!().imul_imm($pv, a0 as i64);
+			// 	let pv = ins!().iadd_imm(pv, b0 as i64);
+			// 	let pv = ins!().imul_imm(pv, a1 as i64);
+			// 	let pv = ins!().iadd_imm(pv, b1 as i64);
+			// 	pv
+			// } else
+			{
 				let (coeffs, inv_coeffs) = generate_polynomial_maps!($ty, $olevel);
+				// let (coeffs, inv_coeffs) = generate_polynomial_maps!($ty, 1);
 				let x = $pv;
 				let mut px = ins!().iconst($tyv, coeffs[0] as i64); // a0
 				for i in 1..=$olevel {
@@ -176,7 +178,8 @@ fn blur_value(fb: &'_ mut FunctionBuilder, val: Value) -> Value {
 	}
 
 	let mut acc_val = ins!().iconst(val_ty, 0);
-	let olevel = heavy();
+	// let olevel = heavy();
+	let olevel = 1;
 	for ty in random_type_partition {
 		let pv = ins!().ushr_imm(val, offset);
 		// let pv = ins!().ireduce(ty, pv);
@@ -194,12 +197,13 @@ fn blur_value(fb: &'_ mut FunctionBuilder, val: Value) -> Value {
 		};
 
 		let pv = if ty.bytes() < fb.func.dfg.value_type(val).bytes() {
-			fb.ins().uextend(val_ty, pv)
+			ins!().uextend(val_ty, pv)
 		} else {
 			pv
 		};
-		let pv = fb.ins().ishl_imm(pv, offset);
[…]

### 2020-03-02 src/backend/function.rs
update

@@ -21,7 +21,7 @@ use cranelift_preopt::optimize;
 use target_lexicon::triple;
 
 use crate::{
-	checked_if_let, checked_match, checked_unwrap_option, checked_unwrap_result,
+	checked_if_let, checked_match, checked_unwrap_option, checked_unwrap_result, disabled,
 	frontend::syntax::{
 		BinaryOperator, BinaryOperatorExpression, CallExpression, Declaration, Declarator,
 		DerivedDeclarator, DoWhileStatement, Expression, ForStatement, FunctionDeclarator,
@@ -93,8 +93,15 @@ fn masquerade_function_signature(
 	return_ty: Option<Type>, param_ty: &'_ [Type], topty: Type,
 ) -> Signature {
 	Signature {
-		params: param_ty.iter().map(|_| AbiParam::new(topty)).collect(),
-		returns: if return_ty.is_some() { vec![AbiParam::new(topty)] } else { vec![] },
+		params: param_ty
+			.iter()
+			.map(|ty| if disabled() { AbiParam::new(*ty) } else { AbiParam::new(topty) })
+			.collect(),
+		returns: if let Some(return_ty) = return_ty {
+			vec![if disabled() { AbiParam::new(return_ty) } else { AbiParam::new(topty) }]
+		} else {
+			vec![]
+		},
 		call_conv: isa::CallConv::SystemV,
 	}
 }
@@ -119,15 +126,15 @@ fn blur_bor(fb: &'_ mut FunctionBuilder, x: Value, y: Value) -> Value {
 }
 
 fn blur_value(fb: &'_ mut FunctionBuilder, val: Value) -> Value {
-	if light() {
-		return val;
-	}
+	// if light() {
+	// 	return val;
+	// }
 
 	let val_ty = fb.func.dfg.value_type(val);
-	let val_size = val_ty.bytes();
+	// let val_size = val_ty.bytes();
 
-	let random_type_partition = generate_random_partition(val_size);
-	let mut offset = 0i64;
+	// let random_type_partition = generate_random_partition(val_size);
+	// let mut offset = 0i64;
 
 	#[rustfmt::skip]
 	macro_rules! ins {
@@ -177,74 +184,92 @@ fn blur_value(fb: &'_ mut FunctionBuilder, val: Value) -> Value {
 		};
 	}
 
-	let mut acc_val = ins!().iconst(val_ty, 0);
-	// let olevel = heavy();
[…]

### 2020-03-02 src/main.rs

@@ -37,6 +37,9 @@ struct Opt {
 	#[options(help = "only type flattening, nothing more", no_long)]
 	light: bool,
 
+	#[options(help = "disable all obfuscation", no_long)]
+	disable: bool,
+
 	#[options(
 		help = "type flattening, call aliasing, etc.",
 		meta = "level",
@@ -56,6 +59,9 @@ struct Opt {
 	jit: bool,
 }
 
+static mut DISABLED: bool = false;
+pub fn disabled() -> bool { unsafe { DISABLED } }
+
 static HEAVY_BLUR: OnceCell<u8> = OnceCell::new();
 pub fn heavy() -> u8 { *HEAVY_BLUR.get_or_init(|| 3) }
 
@@ -70,6 +76,7 @@ fn main() {
 	HEAVY_BLUR.set(opt.heavy).unwrap();
 	LIGHT_BLUR.set(opt.light).unwrap();
 	VERBOSE.set(opt.verbose).unwrap();
+	unsafe { DISABLED = opt.disable };
 
 	let src_code = fs::read_to_string(&opt.src).expect("failed to read source code file");
 	let tu = frontend::syntax::parse(src_code.as_str());

### 2020-03-05 demo/nprime.c
update

@@ -1,0 +1,42 @@
+#include <stdio.h>
+
+int isprime(long p) {
+    long d = 1;
+    int ok = 1;
+    int found = 1;
+    while (ok) {
+        d++;
+        if (d * d > p) {
+            ok = 0;
+        } else {
+            if (p % d == 0) {
+                found = 0;
+                ok = 0;
+            }
+        }
+    }
+    return found;
+}
+
+long nprime(int n) {
+    long p = 1;
+    int i = 0;
+    while (i < n) {
+        p++;
+        if (isprime(p)) {
+            i++;
+        }
+    }
+    return p;
+}
+
+int main() {
+    // int i = isprime(8);
+    // if (i == 1) {
+    //     printf("prime\n");
+    // } else {
+    //     printf("not prime\n");
+    // }
+    long p = nprime(1);
+    printf("p = %ld\n", p);
+}

### 2020-03-05 src/main.rs

@@ -184,7 +184,7 @@ mod compilation_tests {
 	}
 
 	// fn(i32) -> i32
-	fn compile_and_run_int_to_int(file: impl AsRef<Path>, fname: &str, i: i32) -> i32 {
+	fn compile_and_run_int_to_int(file: &dyn AsRef<Path>, fname: &str, i: i32) -> i32 {
 		let src = fs::read_to_string(file).expect("failed to read source code file");
 		let tu = frontend::syntax::parse(src.as_str());
 		frontend::semantics::check(&tu);
@@ -197,7 +197,8 @@ mod compilation_tests {
 		unsafe { fptr(i) }
 	}
 
-	fn compile_and_run_int_int_to_int(file: impl AsRef<Path>, fname: &str, i: i32, j: i32) -> i32 {
+	// fn(i32, i32) -> i32
+	fn compile_and_run_int_int_to_int(file: &dyn AsRef<Path>, fname: &str, i: i32, j: i32) -> i32 {
 		let src = fs::read_to_string(file).expect("failed to read source code file");
 		let tu = frontend::syntax::parse(src.as_str());
 		frontend::semantics::check(&tu);
@@ -208,6 +209,34 @@ mod compilation_tests {
 
 		let fptr = unsafe { mem::transmute::<_, unsafe extern "C" fn(i32, i32) -> i32>(fptr) };
 		unsafe { fptr(i, j) }
+	}
+
+	// fn(i64) -> i32
+	fn compile_and_run_long_to_int(file: &dyn AsRef<Path>, fname: &str, i: i64) -> i32 {
+		let src = fs::read_to_string(file).expect("failed to read source code file");
+		let tu = frontend::syntax::parse(src.as_str());
+		frontend::semantics::check(&tu);
+
+		let builder = SimpleJITBuilder::new(cranelift_module::default_libcall_names());
+		let mut am = backend::AbstractMachine::<'_, SimpleJITBackend>::new(&tu, builder);
+		let (fptr, _) = am.compiled_function(fname).unwrap();
+
+		let fptr = unsafe { mem::transmute::<_, unsafe extern "C" fn(i64) -> i32>(fptr) };
+		unsafe { fptr(i) }
+	}
+
+	// fn(i32) -> i64
[…]

### 2020-03-05 tests/22.c

@@ -1,0 +1,29 @@
+int isprime(long p) {
+    long d = 1;
+    int ok = 1;
+    int found = 1;
+    while (ok) {
+        d++;
+        if (d * d > p) {
+            ok = 0;
+        } else {
+            if (p % d == 0) {
+                found = 0;
+                ok = 0;
+            }
+        }
+    }
+    return found;
+}
+
+long nprime(int n) {
+    long p = 1;
+    int i = 0;
+    while (i < n) {
+        p++;
+        if (isprime(p)) {
+            i++;
+        }
+    }
+    return p;
+}

### 2020-03-06 src/backend/function.rs
update

@@ -244,19 +244,29 @@ fn create_entry_block(
 				let val = fb.block_params(trampoline_block)[i];
 				// let val = blur_value(fb, val);
 
-				if ty.bytes() < pointer_ty.bytes() {
-					let ss = fb.create_stack_slot(StackSlotData::new(
-						StackSlotKind::ExplicitSlot,
-						pointer_ty.bytes(),
-					));
-					fb.ins().stack_store(val, ss, 0);
+				let ss = fb.create_stack_slot(StackSlotData::new(
+					StackSlotKind::ExplicitSlot,
+					pointer_ty.bytes(),
+				));
+				fb.ins().stack_store(val, ss, 0);
 
-					let ss_addr = fb.ins().stack_addr(pointer_ty, ss, 0);
-					let ss_addr = blur_value(fb as _, ss_addr);
-					fb.ins().load(*ty, MemFlags::new(), ss_addr, 0)
-				} else {
-					val
-				}
+				let ss_addr = fb.ins().stack_addr(pointer_ty, ss, 0);
+				let ss_addr = blur_value(fb as _, ss_addr);
+				fb.ins().load(*ty, MemFlags::new(), ss_addr, 0)
+
+				// if ty.bytes() < pointer_ty.bytes() {
+				// 	let ss = fb.create_stack_slot(StackSlotData::new(
+				// 		StackSlotKind::ExplicitSlot,
+				// 		pointer_ty.bytes(),
+				// 	));
+				// 	fb.ins().stack_store(val, ss, 0);
+
+				// 	let ss_addr = fb.ins().stack_addr(pointer_ty, ss, 0);
+				// 	let ss_addr = blur_value(fb as _, ss_addr);
+				// 	fb.ins().load(*ty, MemFlags::new(), ss_addr, 0)
+				// } else {
+				// 	val
+				// }
 			};
 			param_vals.push(val);
 		}

### 2020-03-11 src/frontend/semantics.rs
update

@@ -450,19 +450,23 @@ impl<'a> SimpleType<'a> {
 #[derive(Clone, Copy, Debug, PartialEq, Eq, PartialOrd, Ord)]
 pub enum PrimitiveType {
 	Char,
+	UChar,
 	Short,
+	UShort,
 	Int,
+	UInt,
 	Long,
+	ULong,
 }
 
 impl PrimitiveType {
 	pub fn size(&self) -> Option<usize> {
 		use PrimitiveType::*;
 		match self {
-			Char => Some(1),
-			Short => Some(2),
-			Int => Some(4),
-			Long => Some(8),
+			Char | UChar => Some(1),
+			Short | UShort => Some(2),
+			Int | UInt => Some(4),
+			Long | ULong => Some(8),
 		}
 	}
 }
@@ -473,10 +477,16 @@ impl Into<PrimitiveType> for &'_ TypeSpecifier<'_> {
 		use TypeSpecifier::*;
 		match self {
 			CharTy => Char,
+			UCharTy => UChar,
 			ShortTy => Short,
+			UShortTy => UShort,
 			IntTy => Int,
+			UIntTy => UInt,
 			LongTy => Long,
-			_ => unsafe { unreachable_unchecked() },
+			ULongTy => ULong,
+			_ => unsafe {
+				unreachable_unchecked()
+			},
 		}
 	}
 }
@@ -559,7 +569,9 @@ pub fn check_statement<'a>(
 								_ => unimpl!("unsupported lhs"),
 							},
 
-							_ => unsafe { unreachable_unchecked() },
+							_ => unsafe {
+								unreachable_unchecked()
+							},
 						}
 					}
 

### 2020-03-12 src/backend/function.rs
update

@@ -49,7 +49,7 @@ struct FunctionTranslator<'clif: 'tcx, 'tcx, B: Backend> {
 	name_env: NameBindingEnvironment<'tcx>,
 	type_env: TypeBindingEnvironment<'tcx>,
 	pointer_ty: Type,
-	return_ty: Option<Type>,
+	return_ty: Option<CType>,
 }
 
 pub fn get_function_signature(
@@ -78,7 +78,7 @@ pub fn get_function_signature(
 					// some pointer types
 					DerivedDeclarator::Pointer => match specifier {
 						CharTy | ShortTy | IntTy | LongTy => Signed(pointer_ty),
-						UCharTy | UShortTy | UIntTy | LongTy => Unsigned(pointer_ty),
+						UCharTy | UShortTy | UIntTy | ULongTy => Unsigned(pointer_ty),
 						StructTy(_) | VoidTy => todo!(),
 					},
 				}
@@ -99,15 +99,18 @@ pub fn get_function_signature(
 }
 
 fn masquerade_function_signature(
-	return_ty: Option<Type>, param_ty: &'_ [Type], topty: Type,
+	return_ty: Option<CType>, param_ty: &'_ [CType], topty: Type,
 ) -> Signature {
 	Signature {
 		params: param_ty
 			.iter()
-			.map(|ty| if disabled() { AbiParam::new(*ty) } else { AbiParam::new(topty) })
+			.map(|cty| {
+				let ty: Type = cty.into();
+				if disabled() { AbiParam::new(ty) } else { AbiParam::new(topty) }
+			})
 			.collect(),
 		returns: if let Some(return_ty) = return_ty {
-			vec![if disabled() { AbiParam::new(return_ty) } else { AbiParam::new(topty) }]
+			vec![if disabled() { AbiParam::new(return_ty.into()) } else { AbiParam::new(topty) }]
 		} else {
 			vec![]
 		},
@@ -116,7 +119,7 @@ fn masquerade_function_signature(
 }
 
 pub fn blur_function_signature(
-	return_ty: Option<Type>, param_ty: &'_ [Type], pointer_ty: Type, ctxt: &'_ mut Context,
+	return_ty: Option<CType>, param_ty: &'_ [CType], pointer_ty: Type, ctxt: &'_ mut Context,
 ) {
 	let sig = masquerade_function_signature(return_ty, param_ty, pointer_ty);
 	ctxt.func.signature = sig;
[…]

### 2020-03-12 src/backend/support.rs

@@ -83,7 +83,7 @@ impl<'a> Into<AggregateType<'a>> for &'_ StructType<'a> {
 	}
 }
 
-#[derive(Clone, Debug, PartialEq, Eq)]
+#[derive(Clone, Copy, Debug, PartialEq, Eq)]
 pub enum CType {
 	Signed(Type),
 	Unsigned(Type),

### 2020-03-12 src/backend/translation.rs

@@ -8,7 +8,7 @@ use crate::{
 		Declaration, ExternalDeclaration, FunctionDeclarator, FunctionDefinition, Identifier,
 		StructType, TranslationUnit, TypeSpecifier,
 	},
-	semantically_unreachable,
+	semantically_unreachable, disabled
 };
 
 use super::{

### 2020-03-12 src/frontend/semantics.rs

@@ -393,7 +393,7 @@ impl<'a> SimpleType<'a> {
 		match ty {
 			VoidTy => Self::UnitTy,
 
-			CharTy | ShortTy | IntTy | LongTy => Self::PrimitiveTy(ty.into()),
+			CharTy | UCharTy | ShortTy | UShortTy | IntTy | UIntTy | LongTy | ULongTy => Self::PrimitiveTy(ty.into()),
 
 			StructTy(StructType { identifier, declarations }) => {
 				if let Some(declarations) = declarations {

### 2020-03-13 src/backend/function.rs
update

@@ -663,23 +663,38 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 				let new_var;
 				let new_var_ty;
 				if let Some(derived_decl) = derived {
-					match derived_decl {
-						DerivedDeclarator::Pointer => {
-							new_var = declare_variable(
-								self.func_builder.get_mut(),
-								self.pointer_ty,
-								None,
-							);
-							new_var_ty = self.pointer_ty;
-							self.name_env.bind(
-								var_name,
-								PointerIdent(PointerIdentifer {
-									ident: new_var,
-									ty: PointerTy(Box::new(PrimitiveTy(specifier.into()))),
-								}),
-							);
-						}
+					if matches!(derived_decl, DerivedDeclarator::Pointer) {
+						new_var =
+							declare_variable(self.func_builder.get_mut(), self.pointer_ty, None);
+						new_var_ty = self.pointer_ty;
+						self.name_env.bind(
+							var_name,
+							PointerIdent(PointerIdentifer {
+								ident: new_var,
+								ty: PointerTy(Box::new(PrimitiveTy(specifier.into()))),
+							}),
+						);
+					} else {
+						todo!()
 					}
+
+				// match derived_decl {
+				// 	DerivedDeclarator::Pointer => {
+				// 		new_var = declare_variable(
+				// 			self.func_builder.get_mut(),
+				// 			self.pointer_ty,
+				// 			None,
+				// 		);
+				// 		new_var_ty = self.pointer_ty;
+				// 		self.name_env.bind(
+				// 			var_name,
+				// 			PointerIdent(PointerIdentifer {
+				// 				ident: new_var,
+				// 				ty: PointerTy(Box::new(PrimitiveTy(specifier.into()))),
+				// 			}),
+				// 		);
+				// 	}
+				// }
 				} else {
 					if matches!(specifier, VoidTy) {
 						semantically_unreachable!()
@@ -740,22 +755,37 @@ impl<'clif, 'tcx, B: Backend> FunctionTranslator<'clif, 'tcx, B> {
 					let struct_simple_ty = struct_simple_ty.to_owned();
 
 					if let Some(derived_decl) = derived {
-						match derived_decl {
-							DerivedDeclarator::Pointer => {
-								let new_var = declare_variable(
-									self.func_builder.get_mut(),
-									self.pointer_ty,
-									None,
[…]

### 2020-03-13 tests/23.c

@@ -1,0 +1,5 @@
+unsigned int foo(int x, int y) {
+    unsigned int x0 = x;
+    unsigned int y0 = y;
+    return x0/y0 + x/y;
+}
